---
title: "Action Asymmetry Experiment (n = 1008): Field by Level interaction"
pagetitle: "aah | exp | analysis"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))

plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
data_dir <- here::here("data")
input_dir <- here::here(data_dir, "input_exp_n1008")
proc_dir <- here::here(data_dir, "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_a")
analysis_dir <- here::here("analyses", "experiment_n1008")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_a")

use_cached_model_rt <- TRUE
use_cached_model_rt_complex <- TRUE
use_cached_model_acc <- TRUE
use_cached_model_acc_complex <- TRUE
use_cached_model_rt_ehi <- TRUE
use_cached_model_acc_ehi <- TRUE

use_cached_figs <- FALSE


if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
  use_cached_accfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
  use_cached_accfigs <- FALSE
}

use_cached_model_rt <- FALSE
use_cached_model_rt_complex <- FALSE
use_cached_model_acc <- FALSE
use_cached_model_acc_complex <- FALSE
use_cached_model_rt_ehi <- FALSE
use_cached_model_acc_ehi <- FALSE
```

# {.tabset}
```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r}
## Debugging
# aah_long |> colnames()
# aah_summary_all |> colnames()
```


```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all)

#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
acc_subject <- aah |> group_by(subject, field, level, handedness, sample, sample2) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, field, level, acc, handedness, sample, sample2) |>
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")
```

## Demographics {.tabset .tabset-pills}
```{r demo_plot_config}
plot_color = plot_blue
```


#### By handedness group

Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary) |> pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>

```{r ehi_handedness_plot}
## Show distribution of handedness by EHI bin
plot_color = plot_blue

h_data_n <-
  aah_summary |>
  group_by(handedness) |>
  summarize(n = str_c("n = ", as.character(n())))

fig_path <- here(fig_dir, "bin_ehi_keepers3a.png")

if (use_cached_demofigs == FALSE) {
  g <- ggplot(aah_summary, aes(x = ehi)) +
    geom_histogram(
      color = NA,
      fill = plot_color,
      alpha = .8,
      binwidth = 8,
      boundary = 100
    ) +
    labs(x = "EHI") +
    xlim(c(-104, 104)) +
    facet_grid( ~ handedness) +
    geom_text(
      data = h_data_n,
      aes(x = -100, y = 150, label = n),
      hjust = 0,
      colour = "gray20",
      inherit.aes = FALSE,
      parse = FALSE
    ) +
    labs(title = "EHI distribution within each EHI bin (keepers only)")
  
  g <- g |> gg_style_demo() + theme(aspect.ratio = 1 / 1,
                                    axis.title.y = element_blank())
  
  ggsave(fig_path, g, "png", height = 3, width = 6)
}

include_graphics(fig_path)
```


## Field x Level {.tabset .tabset-pills .active}

```{r plot_rt_config}
plot_color <- plot_colors[[5]] # Color for interaction plots with only one color.
```


### EHI righties (n = 378) {.tabset}

```{r}
handedness_subgroup <- "Right"
subgroup_label <- "RH"
```


In all EHI-confirmed righties (EHI > 40), do we see the predicted field by level interaction?
<br>
<br>
***Summary.*** We see the predicted effect, for both reaction time (27.31ms, 95%CI [19.80, 34.82], p < .001) and accuracy (OR = 1.76, 95%CI [1.49, 2.09], p < .001).
<br>
<br>

```{r, child=c(here(analysis_dir, "components", "3a_analyze_FL_rt_EHI.Rmd"))}
```

```{r, child=c(here(analysis_dir, "components", "3a_analyze_FL_acc_EHI.Rmd"))}
```

### EHI mixedies (n = 135) {.tabset}

```{r}
handedness_subgroup <- "Mixed"
subgroup_label <- "MH"
```

In all EHI-confirmed mixed handers (-40 < EHI < +40), do we see a field by level interaction?
<br>
<br>
***Summary.*** We see a smaller effect in the same direction as right handers' for reaction time (21.66ms, 95%CI [9.26, 34.06], p < .001). For accuracy, we see a smaller, non-significant effect in the same direction as right handers' (OR = 1.10, 95%CI [0.82, 1.47], p = .53).
<br>
<br>
```{r, child=c(here(analysis_dir, "components", "3a_analyze_FL_rt_EHI.Rmd"))}
```

```{r, child=c(here(analysis_dir, "components", "3a_analyze_FL_acc_EHI.Rmd"))}
```

### EHI lefties (n = 331) {.tabset}

```{r}
handedness_subgroup <- "Left"
subgroup_label <- "LH"
```

In all EHI-confirmed lefties (EHI < -40), do we see a field by level interaction?
<br>
<br>
***Summary.*** We see a smaller effect in the same direction as right handers' for reaction time (15.64ms, 95%CI [7.58, 23.70], p < .001). For accuracy, we see a larger effect in the same direction as right handers (OR = 1.96, 95%CI [1.63, 2.37], p < .001).
<br>
<br>
```{r, child=c(here(analysis_dir, "components", "3a_analyze_FL_rt_EHI.Rmd"))}
```

```{r, child=c(here(analysis_dir, "components", "3a_analyze_FL_acc_EHI.Rmd"))}
```
