---
title: "Action Asymmetry Experiment (n = 1008): Shape (Square vs. Circle) Analyses"
pagetitle: "aah | exp | analysis (shape)"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

---
  
# Summary

In pilot analyses (n = 104/112 right handers), we saw a trend towards **stronger LVF global bias for squares** (40.63ms, 95% CI [19.25, 62.00]) than for circles (17.62ms, 95% CI [-3.15, 38.39]; difference = 23.01ms, 95% CI [-6.80, 52.81], p = .13). 

**This pattern was internally replicated**: in the second sample of right handers (204/212) we see a significantly stronger global bias for squares (38.144ms, 95% CI [23.80, 52.49]) than for circles (17.76ms, 95% CI [3.71, 31.81]; difference = 20.382ms, 95% CI [0.31, 40.47], p = .047, two-sided).

In the full sample of EHI right handers (n = 371), we see a significantly stronger global bias for squares (37.66ms, 95% CI [27.00, 48.32]) than for circles (18.13ms, 95% CI [7.72, 28.56]; difference = 19.52ms, 95% CI [4.61, 34.43], p = .01, two-sided).

For *categorical handedness*, there is no significant 4-way interaction, but **the trend is towards a larger 3-way interaction for squares** (difference = 15.89ms, 95% CI [-5.99, 37.76], p = .08, one-sided). For squares, we see a significant 3-way interaction of field by level by handedness (19.76ms, 95% CI [4.11, 35.40], p = .006, one-sided); for circles, we do not see a significant 3-way interaction (3.87ms, 95% CI [-11.41, 19.16], p = .31, one-sided), but the point estimates go in the predicted direction. For both shapes, point estimates suggest reduced, but not reversed, LVF global bias for left handers (+14.27ms for circles, +17.90ms for squares; for right handers, the estimates are +18.13ms for circles, +37.66ms for squares).

For *continuous handedness*, **the trend is again towards a larger 3-way interaction for squares** (difference = 21.02ms from EHI -100 to +100; 95% CI [-4.2ms, 46.0ms], p = .05, one-sided). For squares only, we see a significant 3-way interaction of field by level by handedness (24ms from EHI -100 to +100, 95% CI [6.0, 42.0], p = .004, one-sided). For circles, we do not see a significant 3-way interaction (3.2ms from EHI -100 to +100, 95% CI [-14.4, 20.6], p = .36, one-sided). For both shapes, point estimates suggest reduced, but not reversed LVF global bias for left handers (+15.15ms for circles, +15.25 for squares; for right handers, the estimates are +18.25 for circles, +39.28 for squares).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))
source(here::here("lib", "3c_analyze_shape", "stats.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- here::here("data", "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_c")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_c")

use_cached_models <- T

use_cached_figs <- T

if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
}
```

---

# Analyses {.tabset}
```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all)

#### PREPARE TRIAL-LEVEL DATA FOR RT ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long) |> 
  rename(shape = target)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Code handedness

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))


#### PREPARE SUBJECT_LEVEL DATA FOR RT ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

```

## Field by level by shape {.tabset .tabset-pills}

Reaction time is modeled as a linear effect of field, level, and handedness, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field*level*shape + (1 | subject) )`
<br>
<br>

### Pilot righties (n = 104/112)
<br>
```{r FLS_demo_112RH}
data_label <- "112RH"
data_sub <- aah_for_rt_model |> filter(sample == "Pilot righties")
data_sub_summary <- aah_summary |> filter(sample == "Pilot righties")

FLS_demo <- demo_summary_table(data_sub_summary)
FLS_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLS_model_emm_112RH}
FLS <- model_emm_FLS(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = data_sub,
  data_label = data_label
)
```
<br>
```{r FLS_anova_112RH}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLS(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLS$model,
          title = "Field by level by shape interaction (RT)")
```
<br>
```{r FLS_emmtest_112RH}
## Use emmeans() to test 3-way interaction.
emmtest_FLS(FLS$emm, title = "Field by  level by shape interaction (RT)")
```
<br>
```{r FL_S_emmtest_112RH}
## Estimate interaction of field by level for  shape
emmtest_FL_S(use_cached_model = use_cached_models,
             manual_cache_dir = manual_cache_dir,
             FLS$model,
             data_label = data_label,
             title = "Effect of field by level for each shape (RT)")
```
<br>
```{r FG_F_S_112RH}
## Estimate global bias by field, for each shape
emmtest_GB_F_S(FLS$emm, data_label, title = "Global bias by field, by shape (RT)")
```
<br>
```{r F_L_S_emmtest_112RH}
emmtest_F_L_S(FLS$emm, data_label, title = "RT estimates by field, level, and shape")
```
<br>

### New righties (n = 204/224)
<br>
```{r FLS_demo_224RH}
data_label <- "224RH"
data_sub <- aah_for_rt_model |> filter(sample == "New righties")
data_sub_summary <- aah_summary |> filter(sample == "New righties")

FLS_demo <- demo_summary_table(data_sub_summary)
FLS_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLS_model_emm_224RH}
FLS <- model_emm_FLS(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = data_sub,
  data_label = data_label
)
```
<br>
```{r FLS_anova_224RH}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLS(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLS$model,
          title = "Field by level by shape interaction (RT)")
```
<br>
```{r FLS_emmtest_224RH}
## Use emmeans() to test 3-way interaction.
emmtest_FLS(FLS$emm, title = "Field by  level by shape interaction (RT)")
```
<br>
```{r FL_S_emmtest_224RH}
## Estimate interaction of field by level for  shape
emmtest_FL_S(use_cached_model = use_cached_models,
             manual_cache_dir = manual_cache_dir,
             FLS$model,
             data_label = data_label,
             title = "Effect of field by level for each shape (RT)")
```
<br>
```{r FG_F_S_224R}
## Estimate global bias by field, for each shape
emmtest_GB_F_S(FLS$emm, data_label, title = "Global bias by field, by shape (RT)")
```
<br>
```{r F_L_S_emmtest_224RH}
emmtest_F_L_S(FLS$emm, data_label, title = "RT estimates by field, level, and shape")
```
<br>

### All Prolific righties (n = 308/336)
<br>
```{r FLS_demo_336RH}
data_label <- "336RH"
data_sub <- aah_for_rt_model |> filter(sample2 == "All righties")
data_sub_summary <- aah_summary |> filter(sample2 == "All righties")

FLS_demo <- demo_summary_table(data_sub_summary)
FLS_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLS_model_emm_336RH}
FLS <- model_emm_FLS(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = data_sub,
  data_label = data_label
)
```
<br>
```{r FLS_anova_336RH}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLS(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLS$model,
          title = "Field by level by shape interaction (RT)")
```
<br>
```{r FLS_emmtest_336RH}
## Use emmeans() to test 3-way interaction.
emmtest_FLS(FLS$emm, title = "Field by  level by shape interaction (RT)")
```
<br>
```{r FL_S_emmtest_336RH}
## Estimate interaction of field by level for  shape
emmtest_FL_S(use_cached_model = use_cached_models,
             manual_cache_dir = manual_cache_dir,
             FLS$model,
             data_label = data_label,
             title = "Effect of field by level for each shape (RT)")
```
<br>
```{r FG_F_S_336RH}
## Estimate global bias by field, for each shape
emmtest_GB_F_S(FLS$emm, data_label, title = "Global bias by field, by shape (RT)")
```
<br>
```{r F_L_S_emmtest_336RH}
emmtest_F_L_S(FLS$emm, data_label, title = "RT estimates by field, level, and shape")
```
<br>

### EHI righties (n = 372)
<br>
```{r FLS_demo_378RH}
data_label <- "378RH"
data_sub <- aah_for_rt_model |> filter(handedness == "Right")
data_sub_summary <- aah_summary |> filter(handedness == "Right")

FLS_demo <- demo_summary_table(data_sub_summary)
FLS_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLS_model_emm_378RH}
FLS <- model_emm_FLS(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = data_sub,
  data_label = data_label
)
```
<br>
```{r FLS_anova_378RH}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLS(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLS$model,
          title = "Field by level by shape interaction (RT)")
```
<br>
```{r FLS_emmtest_378RH}
## Use emmeans() to test 3-way interaction.
emmtest_FLS(FLS$emm, title = "Field by  level by shape interaction (RT)")
```
<br>
```{r FL_S_emmtest_378RH}
## Estimate interaction of field by level for  shape
emmtest_FL_S(use_cached_model = use_cached_models,
             manual_cache_dir = manual_cache_dir,
             FLS$model,
             data_label = data_label,
             title = "Effect of field by level for each shape (RT)")
```
<br>
```{r FG_F_S_378RH}
## Estimate global bias by field, for each shape
emmtest_GB_F_S(FLS$emm, data_label, title = "Global bias by field, by shape (RT)")
```
<br>
```{r F_L_S_emmtest_378RH}
emmtest_F_L_S(FLS$emm, data_label, title = "RT estimates by field, level, and shape")
```
<br>


### EHI lefties (n = 331)
<br>
```{r FLS_demo_331LH}
data_label <- "331LH"
data_sub <- aah_for_rt_model |> filter(handedness == "Left")
data_sub_summary <- aah_summary |> filter(handedness == "Left")

FLS_demo <- demo_summary_table(data_sub_summary)
FLS_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLS_model_emm_331LH}
FLS <- model_emm_FLS(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = data_sub,
  data_label = data_label
)
```
<br>
```{r FLS_anova_331LH}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLS(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLS$model,
          title = "Field by level by shape interaction (RT)")
```
<br>
```{r FLS_emmtest_331LH}
## Use emmeans() to test 3-way interaction.
emmtest_FLS(FLS$emm, title = "Field by  level by shape interaction (RT)")
```
<br>
```{r FL_S_emmtest_331LH}
## Estimate interaction of field by level for  shape
emmtest_FL_S(use_cached_model = use_cached_models,
             manual_cache_dir = manual_cache_dir,
             FLS$model,
             data_label = data_label,
             title = "Effect of field by level for each shape (RT)")
```
<br>
```{r FG_F_S_331LH}
## Estimate global bias by field, for each shape
emmtest_GB_F_S(FLS$emm, data_label, title = "Global bias by field, by shape (RT)")
```
<br>
```{r F_L_S_emmtest_331LH}
emmtest_F_L_S(FLS$emm, data_label, title = "RT estimates by field, level, and shape")
```
<br>



## Field by level by handedness by shape {.tabset .tabset-pills}

### Binned handedness

Reaction time is modeled as a linear effect of field, level, handedness (EHI < -40 or EHI > +40), and shape, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field * level * handedness * shape + (1 | subject) )`
<br>
<br>
```{r FLSH_demo_2bins}
data_label <- "2bins"
data_sub <- aah_for_rt_model |> filter(handedness %in% c("Right", "Left"))
data_sub_summary <- aah_summary |> filter(handedness %in% c("Right", "Left"))

FLS_demo <- hand_demo_summary_table(data_sub_summary)
FLS_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLSH_model_emm_2bins}
FLSH <- model_emm_FLSH(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = data_sub,
  data_label = data_label
)
```
<br>
```{r FLSH_anova_2bins}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLSH(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLSH$model,
          title = "4-way field by level by handedness by shape interaction (RT)")
```
<br>
```{r FLSH_emmtest_2bins}
## Use emmeans() to test 4-way interaction.
emmtest_FLSH(FLSH$emm, title = "4-way field by level by handedness by shape interaction (RT)")
```
<br>
```{r FL_SH_emmtest_2bins}
## Estimate the 3-way interaction of field by level by handedness, for each shape
emmtest_FLH_S(use_cached_model = use_cached_models,
             manual_cache_dir = manual_cache_dir,
             FLSH$model,
             data_label = data_label,
             title = "Effect of field by level by handedness for each shape (RT)")
```
<br>
```{r FL_H_S_2bins}
## Estimate the field by level interaction, for each handedness group, for each shape.
emmtest_FL_H_S(use_cached_model = use_cached_models,
               manual_cache_dir = manual_cache_dir,
               FLSH$emm,
               data_label = data_label,
               title = "Effect of field by level for each handedness group, by shape (RT)")
```
<br>

### Continuous handedness
Model RT as a linear effect of field, level, EHI, and shape (continuous):
<br>
<br>
`rt_model_ehi <- lmer( rt ~ field*level*ehi + (1 | subject) )`
<br>
<br>
```{r}
## Prepare data, so emmeans contrasts show
## Global bias as a positive number.
aah_for_rt_ehi_model <- aah_for_rt_model |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("LVF", "RVF")))
```
```{r FLSehi_demo}
data_label <- "ehi"
FLSehi_demo <- hand_demo_summary_table(aah_summary)
FLSehi_demo |> pretty_table() |> tab_header(title = "Demographics")
```
<br>
```{r FLSehi_model_emm}
FLSehi <- model_emm_FLSehi(
  use_cached_model = use_cached_models,
  manual_cache_dir = manual_cache_dir,
  data = aah_for_rt_ehi_model,
  data_label = data_label
)
```
<br>
```{r FLSehi_anova}
## ANOVA: is there a significant interaction of field by level by shape?
anova_FLSehi(use_cached_anova = use_cached_models,
          manual_cache_dir = manual_cache_dir,
          data_label = data_label,
          FLSehi$model,
          title = "4-way field by level by EHI by shape interaction (RT)")
```
<br>
```{r FLSehi_emmtest}
## Use emmeans() to test 4-way interaction.
emmtest_FLSehi(use_cached_model = use_cached_models,
               manual_cache_dir = manual_cache_dir,
               FLSehi_model = FLSehi$model,
               data_label = data_label,
               title = "4-way field by level by EHI by shape interaction (RT)")
```
<br>
```{r FLehi_S_emmtest}
## What is the estimated 3-way interaction effect for each shape?
emmtest_FLehi_S(use_cached_model = use_cached_models,
               manual_cache_dir = manual_cache_dir,
               FLSehi_model = FLSehi$model,
               data_label = data_label,
               title = "3-way interaction effect by shape")

```
<br>

#### Estimated effects for strong left and right handers

<br>
<br>
```{r}
## Effect of shape on LVF global bias by EHI
pull_ehi_FLS(use_cached_model = use_cached_models,
              manual_cache_dir = manual_cache_dir,
              FLSehi_model <- FLSehi$model,
              data_label = data_label,
              title = "Estimated effect of shape on LVF global bias, by EHI score")

```
<br>
```{r}
## Magnitude of LVF global bias by EHI, for each shape.
pull_ehi_FL_S(use_cached_model = use_cached_models,
              manual_cache_dir = manual_cache_dir,
              FLSehi_model <- FLSehi$model,
              data_label = data_label,
              title = "LVF global bias by EHI, for each shape (RT)")
```






