---
title: "Action Asymmetry Experiment (n = 1008): Field by Level by Handedness Analyses (EHI -100 or +100 only)"
pagetitle: "aah | exp | analysis"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>


---

# Summary

When we limit RT analysis to strong left and right handers with EHI scores of +-100, the critical three-way interaction effect is stronger (23.51ms, 95% CI [7.10, 39.92], p = .0025, one-sided), and left handers' LVF global bias is closer to zero (4.59ms (95% CI [-7.80, 16.98]; the effect for right handers is 28.10ms, 95% CI [17.34, 38.86]). We still see a null result for accuracy, but the point estimates are now in the predicted direction (OR = 1.10, 95% CI [0.75, 1.61], p = .32, one-sided; where OR < 1 means greater LVF global bias for left handers).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- here::here("data", "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_d")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_d")

use_cached_model_rt <- T
use_cached_model_acc <- T

use_cached_figs <- T

if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
  use_cached_accfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
  use_cached_accfigs <- FALSE
}
```

---

# Analyses {.tabset}
```{r load_data}
## Load "the data" with all subjects & trials. Filter to only subjects with EHI -100 or +100.
# aah_long <- load_aah_long(proc_dir) |> filter(ehi %in% c(-100, 100))
aah_long <- load_aah_long(proc_dir) |> mutate(
  handedness = case_when(
    ehi == -100 ~ "Left",
    ehi == 100 ~ "Right",
    ehi > -100 & ehi < 100 ~ "Mixed")
)

## Load summary data table (for quick demographic analyses)
## with all subjects.
# aah_summary_all <- load_aah_summary(proc_dir) |> filter(ehi %in% c(-100, 100))
aah_summary_all <- load_aah_summary(proc_dir) |> mutate(
  handedness = case_when(
    ehi == -100 ~ "Left",
    ehi == 100 ~ "Right",
    ehi > -100 & ehi < 100 ~ "Mixed")
) 
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all)

#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Code handedness

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("RVF", "LVF")))

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
acc_subject <- aah |> group_by(subject, field, level, handedness) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, handedness, field, level, acc) |>
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")

```

## Demographics {.tabset .tabset-pills}

Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary) |> pretty_table() |>
  tab_footnote("Left: (EHI = -100)  | Right: (EHI = +100) | Mixed: Everyone in between")
```
<br>
```{r demo_plot_ehi_binned}
plot_color = plot_blue
fig_path <- here(fig_dir, "demo_ehi_binned.png")

if (use_cached_demofigs == FALSE) {
g <- ggplot(aah_summary, aes(x = ehi)) +
  geom_histogram(color = NA, fill = plot_color, alpha = .8, binwidth = 8, boundary = 100) +
  geom_vline(xintercept = -92, color = plot_colors[[2]]) +
  geom_vline(xintercept = 92, color = plot_colors[[2]]) +
  labs(x = "EHI")

g <- g |> gg_style_demo() + theme(aspect.ratio = 1/2,
                            axis.title.y = element_blank())

ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
```



## Field x Level x Handedness (binned) {.tabset .tabset-pills}

Do we find an interaction of field x level x handedness, when handedness is binned as left (EHI = -100) or right (EHI = +100)?
<br>
<br>

 ***Summary.*** For reaction time, we find the critical interaction in the predicted direction (23.51ms, 95% CI [7.10, 39.92], p = .0025, one-sided). Left handers show 4.59ms LVF global bias (95% CI [-7.80, 16.98]), and right handers 28.10ms (95% CI [17.34, 38.86]). Mixed handers (not included in the categorical interaction analysis) show a LVF global bias of 24.195ms (95% CI [17.82, 30.58]).
 
For accuracy, we find no significant interaction of field by level by handedness (OR = 1.10, 95% CI [0.75, 1.61], p = .32, one-sided; where OR < 1 means greater LVF global bias for left handers). Point estimates of LVF global bias hardly differ between left handers (OR = 1.67, 95% CI [1.26, 2.22]) and right handers (OR = 1.84, 95% CI [1.42, 2.38]). For mixed handers (not included in the categorical interaction analysis), the point estimate is 1.67 (95% CI [1.44, 1.93]).

<br>
<br>

### Reaction time {.tabset}

#### Plots

Error bars show 95% CI. Left handers are those with EHI = -100; Right handers, EHI = +100. "Mixed handers" are everyone with EHI values in between -100 and +100.
```{r plot_rt_config}
plot_color <- plot_colors[[5]] # Color for interaction plots with only one color.
```

```{r plot_rt_4a_all_trials}
## Plot data from every trial, with overall mean, median and bounds.
fig_path_rt_4a <- here(fig_dir, "rt_4a.png")

if (use_cached_rtfigs == FALSE) {
rt_descriptive <- aah_correct |>
  group_by(field, level, handedness) |>
  summarize(
    median = median(rt),
    mean = mean(rt),
    SE = sd(rt) / sqrt(length((rt)))
  )

## Facet by: Visual field, handedness
g <- ggplot(aah_correct, aes(
  x = level,
  y = rt,
  fill = level,
  color = level,
)) +
  geom_quasirandom(alpha = .05, show.legend = F) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .3,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(data = rt_descriptive, aes(y = mean), color = "black", shape = 21,
             show.legend = F) +
  scale_y_continuous(minor_breaks = seq(0 , 2000, 100),
                     breaks = seq(0, 2000, 200)) +
  facet_grid(vars(handedness), vars(field)) +
  labs(title = "All trials (RT)", x = "Level", y = "Reaction time (ms)")

g <- g |> gg_style_means() |> gg_color()
ggsave(fig_path_rt_4a, g, "png", height = 8, width = 4)
g_rt_4a <- g
}

include_graphics(fig_path_rt_4a)
```
<br>

---

<br>
```{r plot_rt_4}
fig_path_rt_4 <- here(fig_dir, "rt_4.png")

if (use_cached_rtfigs == FALSE) {
rt_subject <- aah_correct |>
  group_by(subject, field, level, handedness) |> 
  summarize(rt = median(rt))

rt_descriptive <- rt_subject |>
  group_by(field, level, handedness) |>
  summarize(
    median = median(rt),
    mean = mean(rt),
    SE = sd(rt) / sqrt(length((rt)))
  )

g <- ggplot(rt_subject, aes(
  x = level,
  y = rt,
  fill = level,
  color = level
)) +
  geom_quasirandom(alpha = .1, show.legend = F) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = rt_descriptive,
    aes(y = mean),
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(0 , 1500, 100),
                     breaks = seq(0, 1500, 200)) +
  facet_grid(vars(handedness), vars(field)) +
  labs(title = "Per-subject medians (RT)", x = "Level", y = "Reaction time (ms)")

g <- g |>  gg_style_means() |> gg_color()
ggsave(fig_path_rt_4, g, "png", height = 8, width = 4)
g_rt_4 <- g
}

include_graphics(fig_path_rt_4)
```

---

```{r plot_rt_2}
fig_path_rt_2 <- here(fig_dir, "rt_2.png")

if (use_cached_rtfigs == FALSE) {
## Make a table showing:
## For each subject and field, the difference in median rt for:
## Global - Local
rt_2 <- rt_subject |> 
  pivot_wider(names_from = c(level),
              values_from = rt) |> 
  mutate(Global_Bias = Local - Global)

rt_descriptive <- rt_2 |>
  group_by(field, handedness) |>
  summarize(
    median = median(Global_Bias),
    mean = mean(Global_Bias),
    SE = sd(Global_Bias) / sqrt(length((Global_Bias)))
  )

g <- ggplot(rt_2, aes(x = field,
                      y = Global_Bias, fill = handedness, color = handedness)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    # color = plot_color
    ) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    # fill = plot_color,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    show.legend = F
  ) +
  geom_point(
    data = rt_descriptive,
    aes(y = mean),
    # fill = plot_color,
    color = "gray5",
    shape = 21,
    show.legend = F
  ) +
  facet_wrap(~handedness)+
  scale_y_continuous(minor_breaks = seq(-500 , 500, 50),
                     breaks = seq(-500, 500, 100)) +
  scale_fill_manual(values = plot_colors[c(1, 5,  2)]) +
  scale_color_manual(values = plot_colors[c(1, 5,  2)]) +
  labs(title = "Global bias (RT)", x = "Level", y = "Local - Global RT (ms)")

g <- g |> gg_style_means()
ggsave(fig_path_rt_2, g, "png", height = 4, width = 4)
g_rt_2 <- g
}
include_graphics(fig_path_rt_2)
```

---

```{r plot_rt_1}
fig_path_rt_1 <- here(fig_dir, "rt_1.png")

if (use_cached_rtfigs == FALSE) {
  ## Make a table showing:
  ## For each subject and field, the difference in median rt for:
  ## Global - Local
  rt_1 <- rt_subject |>
    pivot_wider(names_from = c(field, level),
                values_from = rt) |>
    mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
    mutate(all_one_group = "all_one_group")
    
rt_descriptive <- rt_1 |>
  group_by(all_one_group, handedness) |> 
  summarize(
    median = median(LVF_Global_Bias),
    mean = mean(LVF_Global_Bias),
    SE = sd(LVF_Global_Bias) / sqrt(length((LVF_Global_Bias)))
  )

g <- ggplot(rt_1, aes(
  x = all_one_group,
  y = LVF_Global_Bias,
  fill = handedness,
  color = handedness
)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    # color = plot_color
    ) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    # fill = plot_color,
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = rt_descriptive,
    aes(y = mean),
    # fill = plot_color,
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  facet_wrap(~handedness) +
  scale_y_continuous(minor_breaks = seq(-500 , 500, 50),
                     breaks = seq(-500, 500, 100)) +
  scale_fill_manual(values = plot_colors[c(1, 5,  2)]) +
  scale_color_manual(values = plot_colors[c(1, 5,  2)]) +
  theme(axis.text.x = element_blank()) +
  labs(title = "LVF>RVF Global Bias (RT)", x = "Level", y = "RVF - LVF, Local - Global RT (ms)")

g <- g |> gg_style_means() +
  theme(axis.text.x = element_blank(), aspect.ratio = 4/1)
ggsave(fig_path_rt_1, g, "png", height = 4, width = 4)
g_rt_1 <- g
}

include_graphics(fig_path_rt_1)
```


#### Statistics

##### Simple mixed regression model
Reaction time is modeled as a linear effect of field, level, and handedness, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field*level*handedness + (1 | subject) )`
<br>
<br>

```{r rt_model_2bins}
## Make a model with two handedness bins: Right and Left
aah_for_rt_model_2bins <- aah_for_rt_model |> filter(handedness %in% c("Right", "Left"))
rt_model_2bins <- lmer(rt ~ field*level*handedness + (1 | subject), data = aah_for_rt_model_2bins)

if (use_cached_model_rt == FALSE) {
  ## Create emmeans model object, and manually cache it.
  rt_emm_2bins <- emmeans(rt_model_2bins, ~ field * level * handedness)
  ## Todo: run without z-approximation:
  # rt_emm <- emmeans(rt_model, ~ field * level * handedness, pbkrtest.limit = 59851)
  
  ## Manually cache model
  saveRDS(rt_emm_2bins, here(manual_cache_dir, "rt_emm_2bins.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_emm_2bins <- readRDS(here(manual_cache_dir, "rt_emm_2bins.rds"))
}
```
```{r}
## Make a model with three handedness bins: Right, Left, Mixed

if (use_cached_model_rt == FALSE) {
  rt_model_3bins <-
    lmer(rt ~ field * level * handedness + (1 |
                                              subject), data = aah_for_rt_model)
  ## Create emmeans model object, and manually cache it.
  rt_emm_3bins <-
    emmeans(rt_model_3bins, ~ field * level * handedness)
  ## Todo: run without z-approximation:
  # rt_emm <- emmeans(rt_model, ~ field * level * handedness, pbkrtest.limit = 59851)
  
  ## Manually cache model
  saveRDS(rt_model_3bins, here(manual_cache_dir, "rt_model_3bins.rds"))
  saveRDS(rt_emm_3bins, here(manual_cache_dir, "rt_emm_3bins.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_model_3bins <-
    readRDS(here(manual_cache_dir, "rt_model_3bins.rds"))
  rt_emm_3bins <- readRDS(here(manual_cache_dir, "rt_emm_3bins.rds"))
}
```
```{r}
## Make a model with three handedness bins: Strong/weak Right/Left
aah_for_rt_model_4bins <- aah_for_rt_model |> 
  mutate(handedness = case_when(
    ehi == -100 ~ "Strong Left",
    ehi > -100 & ehi <= 0 ~ "Weak Left",
    ehi > 0 & ehi < 100 ~ "Weak Right",
    ehi == 100 ~ "Strong Right"
  )) |> 
  mutate(handedness = factor(handedness, levels = c("Strong Left", "Weak Left", "Weak Right", "Strong Right")))

if (use_cached_model_rt == FALSE) {
  rt_model_4bins <-
    lmer(rt ~ field * level * handedness + (1 |
                                              subject), data = aah_for_rt_model_4bins)
  ## Create emmeans model object, and manually cache it.
  rt_emm_4bins <-
    emmeans(rt_model_4bins, ~ field * level * handedness)
  ## Todo: run without z-approximation:
  # rt_emm <- emmeans(rt_model, ~ field * level * handedness, pbkrtest.limit = 59851)
  
  ## Manually cache model
  saveRDS(rt_model_4bins, here(manual_cache_dir, "rt_model_4bins.rds"))
  saveRDS(rt_emm_4bins, here(manual_cache_dir, "rt_emm_4bins.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_model_4bins <- readRDS(here(manual_cache_dir, "rt_model_4bins.rds"))
  rt_emm_4bins <- readRDS(here(manual_cache_dir, "rt_emm_4bins.rds"))
}
```


<br>
```{r rt_interaction_anova}
## Use anova() on competing models to test 2-way interaction.
interaction_stats <-
  function(model_with_interaction,
           model_with_no_interaction) {
    return(anova(model_with_interaction, model_with_no_interaction))
  }

rt_model_no_interaction <- update(rt_model_2bins, . ~ . - field:level:handedness)
interaction_anova <- interaction_stats(rt_model_2bins, rt_model_no_interaction)
interaction_anova |>
  as_tibble() |>
  rename(p.value = `Pr(>Chisq)`) |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Field by level by handedness interaction (RT)", 
             subtitle = "ANOVA: compare models with vs. without interaction term") |> 
  tab_footnote(footnote = "F-test (two-sided? https://daniellakens.blogspot.com/2016/04/one-sided-f-tests-and-halving-p-values.html)",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r rt_interaction_emm}
## Use emmeans() to test 3-way interaction.
rt_interaction_emm <- rt_emm_2bins |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T)

rt_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level by handedness interaction (RT)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means LVF global bias is stronger in right handers (as predicted by AAH)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_handedness_bias}
## Estimate the effect of field by level for each handedness group
rt_emm2 <- emmeans(rt_model_2bins, ~field*level | handedness) |>
  contrast(interaction = "consec") |>
  summary(infer = T, adj = "none")

rt_emm2 |>
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "LVF Global bias by handedness bin (RT)") |>
  tab_footnote(footnote = "A positive number means global bias (faster RT for global)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_handedness_bias_3bins}
## Estimate the effect of field by level for each handedness group
rt_emm2 <- emmeans(rt_model_3bins, ~field*level | handedness) |>
  contrast(interaction = "consec") |>
  summary(infer = T, adj = "none")

rt_emm2 |>
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "LVF Global bias by handedness bin, including mixed (RT)") |>
  tab_footnote(footnote = "A positive number means global bias (faster RT for global)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Left: EHI = -100; Right: EHI = +100; Mixed: Everyone else. These mixed handers were not included in the model.",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_handedness_bias_4bins}
## Estimate the effect of field by level for each handedness group
rt_emm2 <- emmeans(rt_model_4bins, ~field*level | handedness) |>
  contrast(interaction = "consec") |>
  summary(infer = T, adj = "none")

rt_emm2 |>
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "LVF Global bias by handedness bin, including mixed (RT)") |>
  tab_footnote(footnote = "A positive number means global bias (faster RT for global)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Strong left: EHI = -100; Weak left: -100 < EHI <= 0; Weak right: 0 < EHI < +100; Strong right: EHI = +100. These mixed handers were not included in the model.",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_handedness_bias_field}
## Estimate Global bias in each field, fir right and left handers
rt_emm_2bins |> contrast(interaction = "consec", by = c("field", "handedness")) |> 
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Global bias by field, by handedness bin (RT)") |>
  tab_footnote(footnote = "A positive number means global bias (faster RT for global)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>
```{r}
## Estimate RT by level, field, handedness.
rt_emm_2bins |> 
  as_tibble() |> 
  pretty_table() |> 
  tab_header(title = "RT (ms) by field, level and handedness bin") |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
  
```
<br>

---

<br>
```{r rt_interacion_aov}
## Use aov to test 2-way interaction with a traditional F-test.
rt_aov <- aov(rt ~ field*level*handedness, data = aah_for_rt_model_2bins)
rt_aov_summary <- summary(rt_aov)
rt_aov_summary |> (\(.) .[[1]])() |> tidy() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (RT)",
             subtitle = "Old-school Omnibus F-test")
```
<br>

---

<br>
```{r, echo = T, results = "markup"}
summary(rt_model_2bins)
```
<br>


### Accuracy {.tabset .active}

#### Plots

Error bars show 95% CI. Left handers are those with EHI = -100; Right handers, EHI = +100. "Mixed handers" are everyone with EHI values in between -100 and +100.
```{r plot_acc_config}
plot_color <- plot_colors[[5]] # Color for interaction plots with only one color.
```
<br>
```{r plot_acc_4}
fig_path_acc_4 <- here(fig_dir, "acc_4.png")

if (use_cached_accfigs == FALSE) {

acc_descriptive <- acc_subject |>
  group_by(field, level, handedness) |>
  summarize(
    median = median(acc),
    mean = mean(acc),
    SE = sd(acc) / sqrt(length((acc)))
  )

g <- ggplot(acc_subject, aes(
  x = level,
  y = acc,
  fill = level,
  color = level
)) +
  geom_quasirandom(alpha = .1, show.legend = F) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = acc_descriptive,
    aes(y = mean),
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(-100 , 100, 10),
                     breaks = seq(-100, 100, 20)) +
  facet_grid(vars(handedness), vars(field)) +
  labs(title = "Per-subject accuracy", x = "Level", y = "Accuracy (% correct)")

g <- g |>  gg_style_means() |> gg_color()
ggsave(fig_path_acc_4, g, "png", height = 8, width = 4)
g_acc_4 <- g
}

include_graphics(fig_path_acc_4)
```

---

```{r plot_acc_2}
fig_path_acc_2 <- here(fig_dir, "acc_2.png")

if (use_cached_accfigs == FALSE) {
## Make a table showing:
## For each subject and field, the difference in median acc for:
## Global - Local
acc_2 <- acc_subject |> 
  pivot_wider(names_from = c(level),
              values_from = acc) |> 
  mutate(Global_Bias = Global - Local)

acc_descriptive <- acc_2 |>
  group_by(field, handedness) |>
  summarize(
    median = median(Global_Bias),
    mean = mean(Global_Bias),
    SE = sd(Global_Bias) / sqrt(length((Global_Bias)))
  )

g <- ggplot(acc_2, aes(x = field,
                      y = Global_Bias, fill = handedness, color = handedness)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    # color = plot_color
    ) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    # fill = plot_color,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    show.legend = F
  ) +
  geom_point(
    data = acc_descriptive,
    aes(y = mean),
    # fill = plot_color,
    color = "gray5",
    shape = 21,
    show.legend = F
  ) +
  facet_wrap(~handedness)+
  scale_y_continuous(minor_breaks = seq(-100 , 100, 10),
                     breaks = seq(-100, 100, 20)) +
  scale_fill_manual(values = plot_colors[c(1, 5,  2)]) +
  scale_color_manual(values = plot_colors[c(1, 5,  2)]) +
  labs(title = "Global bias (Accuracy)", x = "Level", y = "Global - Local Accuracy (% correct)")

g <- g |> gg_style_means()
ggsave(fig_path_acc_2, g, "png", height = 4, width = 4)
g_acc_2 <- g
}

include_graphics(fig_path_acc_2)
```

---

```{r plot_acc_1}
fig_path_acc_1 <- here(fig_dir, "acc_1.png")

if (use_cached_accfigs == FALSE) {
  ## Make a table showing:
  ## For each subject and field, the difference in median acc for:
  ## Global - Local
  acc_1 <- acc_subject |>
    pivot_wider(names_from = c(field, level),
                values_from = acc) |>
    mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
    mutate(all_one_group = "all_one_group")
  
  acc_descriptive <- acc_1 |>
    group_by(all_one_group, handedness) |>
    summarize(
      median = median(LVF_Global_Bias),
      mean = mean(LVF_Global_Bias),
      SE = sd(LVF_Global_Bias) / sqrt(length((LVF_Global_Bias)))
    )
  
  g <- ggplot(acc_1, aes(
    x = all_one_group,
    y = LVF_Global_Bias,
    fill = handedness,
    color = handedness
  )) +
    geom_quasirandom(
      alpha = .1, show.legend = F,
      # color = plot_color
      ) +
    geom_boxplot(
      alpha = 0.5,
      size = 0.3,
      varwidth = F,
      outlier.shape = NA,
      color = "gray20",
      # fill = plot_color,
      show.legend = F
    ) +
    stat_summary(
      fun.data = mean_cl_normal,
      fun.args = list(conf.int = 0.95),
      geom = "errorbar",
      position = "dodge",
      linetype = 1,
      color = "gray5",
      width = .2,
      # size = point_size / 5,
      show.legend = F
    ) +
    geom_point(
      data = acc_descriptive,
      aes(y = mean),
      # fill = plot_color,
      color = "black",
      shape = 21,
      show.legend = F
    ) +
    facet_wrap(~handedness) +
    # scale_y_continuous(minor_breaks = seq(-500 , 500, 50),
    #                    breaks = seq(-500, 500, 100)) +
    scale_fill_manual(values = plot_colors[c(1, 5,  2)]) +
    scale_color_manual(values = plot_colors[c(1, 5,  2)]) +
    theme(axis.text.x = element_blank()) +
    labs(title = "LVF>RVF Global Bias (Accuracy)", x = "Level", y = "LVF - RVF, Global - Local Accuracy (% correct)")
  
g <- g |> gg_style_means() +
  theme(axis.text.x = element_blank(), aspect.ratio = 4/1)
ggsave(fig_path_acc_1, g, "png", height = 4, width = 4)
g_acc_1 <- g
}

include_graphics(fig_path_acc_1)
```

#### Statistics
##### Simple mixed regression model

Accuracy is modeled as a binomial effect of field, level, and handedness, using binary correct/incorrect data from every target-present trial:
<br>
<br>
`glmer( correct ~ field*level*handedness + (1 | subject), family = "binomial" )`
<br>
<br>
```{r acc_model_2bins}
## Make a binomial logistic model using data from every trial.

if (use_cached_model_acc == FALSE) {
  ## Make a model with two handedness bins: Right and Left
  aah_for_acc_model_2bins <-
    aah_for_acc_model |> filter(handedness %in% c("Right", "Left"))
  
  acc_model_2bins <-
    glmer(correct ~ field * level * handedness + (1 | subject),
          data = aah_for_acc_model_2bins,
          family = "binomial")
  
  ## Warning: the model did not converge
  ## max|grad .006 (tol .002)
  ## https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html
  
  
  ## I re-ran the model with the bobyqa optimizer on Jan 7 2023,
  ## and saw virtually the same estimates.
  # acc_model_2bins <-
  #   glmer(correct ~ field * level * handedness + (1 | subject),
  #         data = aah_for_acc_model_2bins,
  #         family = "binomial",
  #         control = glmerControl(optimizer = c("bobyqa"))
  #         )
  
  
  ## Create emmeans model object, and manually cache it.
  acc_emm_2bins <-
    emmeans(acc_model_2bins, ~ field * level & handedness)
  
  ## Manually cache model
  saveRDS(acc_model_2bins,
          here(manual_cache_dir,
               "acc_model_2bins.rds"))
  saveRDS(acc_emm_2bins, here(manual_cache_dir, "acc_emm_2bins.rds"))
  
} else if (use_cached_model_acc == TRUE) {
  ## Load cached model
  acc_model_2bins <- readRDS(here(manual_cache_dir, "acc_model_2bins.rds"))
  acc_emm_2bins <- readRDS(here(manual_cache_dir, "acc_emm_2bins.rds"))
}
```


```{r}
if (use_cached_model_acc == FALSE) {
  ## Make a model with three handedness bins: Right, Mixed, and Left
  acc_model_3bins <-
    glmer(correct ~ field * level * handedness + (1 | subject),
          data = aah_for_acc_model,
          family = "binomial")
  
  ## Warning message:
  ##In checkConv(attr(opt, "derivs"), opt$par, ctrl = control$checkConv,  :
  ##Model failed to converge with max|grad| = 0.0430293 (tol = 0.002, component 1)
  
  ## Create emmeans model object, and manually cache it.
  acc_emm_3bins <-
    emmeans(acc_model_3bins, ~ field * level * handedness)
  
  ## Manually cache model
  saveRDS(acc_model_3bins,
          here(manual_cache_dir, "acc_model_3bins.rds"))
  saveRDS(acc_emm_3bins, here(manual_cache_dir, "acc_emm_3bins.rds"))
  
} else if (use_cached_model_acc == TRUE) {
  ## Load cached model
  acc_model_3bins <-
    readRDS(here(manual_cache_dir, "acc_model_3bins.rds"))
  acc_emm_3bins <-  readRDS(here(manual_cache_dir, "acc_emm_3bins.rds"))
}
```

<br>
```{r acc_interaction_anova}
## Use anova() on competing models to test 2-way interaction.
if (use_cached_model_acc == FALSE) {
  ## Create and manually cache ANOVA
  acc_model_no_interaction <-
    update(acc_model_2bins, . ~ . - field:level:handedness)
  
  interaction_anova <-
    interaction_stats(acc_model_2bins, acc_model_no_interaction)
  
  ## Manually cache model
  saveRDS(interaction_anova, here(manual_cache_dir,
                                "acc_anova_2bins.rds"))
  
} else if (use_cached_model_acc == TRUE) {
  ## Load cached ANOVA
  interaction_anova <- readRDS(here(manual_cache_dir, "acc_anova_2bins.rds"))
}

interaction_anova |>
  as_tibble() |>
  rename(p.value = `Pr(>Chisq)`) |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Field by level by handedness interaction (Accuracy)", 
             subtitle = "ANOVA: compare models with vs. without interaction term") |> 
  tab_footnote(footnote = "F-test (two-sided? https://daniellakens.blogspot.com/2016/04/one-sided-f-tests-and-halving-p-values.html)",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_interaction_emm}
## Use emmeans() to test 3-way interaction.
acc_interaction_emm <- acc_emm_2bins |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T, type = "response")

acc_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level by handedness interaction (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio > 1 means global bias is stronger in the LVF for right handers (predicted by AAH)",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "'Inf' df is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_handedness_bias}
## Estimate the effect of field by level for each handedness group
acc_emm2 <- emmeans(acc_model_3bins, ~field*level | handedness) |>
  contrast(interaction = "consec") |>
  summary(infer = T, adj = "none", type = "response")

acc_emm2 |>
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "LVF Global bias by handedness bin (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio > 1 means global bias is stronger in the LVF, as predicted for right handers. Mixed handers' global bias is shown here, but their data was not included in the binomial model.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "'Inf' df is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>

---

<br>
```{r, echo = T, results = "markup"}
summary(acc_model_2bins)
```
<br>

