---
title: "Action Asymmetry Experiment (n = 1008): Field by Level by Handedness Analyses (EHI -100 or +100 only)"
pagetitle: "aah | exp | analysis (EHI +/-100)"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>


---

Within each level (local and global): 

(1) Do right and left handers differ in the effect of field?
(2) What is the magnitude of the effect of field, for right and left handers?

(a) For EHI cut at +/- 40
(b) For EHI = +/-100

# Summary

For EHI cut at +/-40:

Right and left handers showed reversed hemifield bias for local stimuli, in the direction predicted by AAH: right handers responded faster to local stimuli in the RVF than LVF by 12.28ms (95%CI [6.93, 17.63], p <.001, two-sided), whereas left handers responded faster to local stimuli in the LVF than RVF by 9.65ms (95% CI [3.91, 15.39], p = .001, two-sided; difference = 21.93ms, 95%CI [4.01, 14.09], p <.001]). For global stimuli, both groups showed significant LVF bias, greater for right handers (15.02ms, 95%CI [9.74, 20.31], p < .001, two-sided) than for left handers (9.65ms, 95%CI [3.91, 15.40], p < .001;  difference = 10.27ms, 95%CI [2.53, 18.00], p = .009, two-sided).

For EHI = +/-100:

Limiting analysis to strong left and right handers (EHI scores +/-100), right handers' RVF bias for local stimuli was 13.56ms (95%CI [5.90, 21.22], p < .001, two-sided), and left handers' LVF bias for local stimuli was 18.09ms (95%CI [9.26, 26.93], p < .001, two-sided; difference = 31.65ms, 95%CI [19.96, 43.35], p < .001). For global stimuli, both groups showed significant LVF bias: 14.54ms for right handers (95%CI [6.99, 22.10], p < .001), and 22.68ms for left handers (95%CI [14.00, 31.37], p < .001; difference = 8.13, 95%CI [-3.37, 19.65], p = .17, two-sided).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- here::here("data", "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_g")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_g")

use_cached_model_rt <- F
use_cached_model_acc <- F
```

# Analyses {.tabset}

```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all) |>
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 & ehi < 100 ~ "Mixed")
  )


#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long) |>
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 &
                                      ehi < 100 ~ "Mixed")
  ) |> rename(shape = target)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Code handedness

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("RVF", "LVF")))

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
acc_subject <- aah |> group_by(subject, field, level, handedness) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, handedness, field, level, acc) |>
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")
```

## EHI cut at +/-40

<br>
<br>
```{r}
hand_demo_summary_table(aah_summary) |> pretty_table("Demographics") |>
  tab_footnote("Left: (EHI = -100)  | Right: (EHI = +100) | Mixed: Everyone in between")
```
<br>
<br>

Reaction time is modeled as a linear effect of field, level, and handedness, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field*level*handedness + (1 | subject) )`
<br>
<br>

```{r rt_model_2bins}
## Make a model with two handedness bins: Right and Left
aah_for_rt_model_2bins <- aah_for_rt_model |> filter(handedness %in% c("Right", "Left"))
rt_model_2bins <- lmer(rt ~ field*level*handedness + (1 | subject), data = aah_for_rt_model_2bins)

if (use_cached_model_rt == FALSE) {
  ## Create emmeans model object, and manually cache it.
  rt_emm_2bins <- emmeans(rt_model_2bins, ~ field * level * handedness)
  ## Todo: run without z-approximation:
  # rt_emm <- emmeans(rt_model, ~ field * level * handedness, pbkrtest.limit = 59851)
  
  ## Manually cache model
  saveRDS(rt_emm_2bins, here(manual_cache_dir, "rt_emm_2bins.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_emm_2bins <- readRDS(here(manual_cache_dir, "rt_emm_2bins.rds"))
}
```

```{r rt_interaction_emm}
## Sanity check: use emmeans() to test 3-way interaction.
rt_interaction_emm <- rt_emm_2bins |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T)

rt_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level by handedness interaction (RT)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means LVF global bias is stronger in right handers (as predicted by AAH)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>

### Within each level (local and global), do right and left handers differ in the effect of field?
```{r}
rt_emm_2bins |> contrast(interaction = "consec", by = c("level")) |> 
  summary(infer = T) |> 
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Interaction of field by handedness, for each level (RT)") |>
  tab_footnote(footnote = "A positive number means more RVF bias for right handers",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>

### Within each level and handedness group, what is the effect of field?

E.g., for local shapes, what is the magnitude of right handers' RVF bias, and left handers' LVF bias?

```{r}
rt_emm_2bins |> contrast("revpairwise", by = c("level", "handedness")) |> 
  summary(infer = T) |> 
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Effect of field, for each level, for each handedness group (RT)") |>
  tab_footnote(footnote = "A positive number means RVF bias; negative, LVF bias",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>





## EHI = +/-100

<br>
<br>
```{r}
hand_extremes_demo_summary_table(aah_summary |> filter(handedness_extremes %in% c("Right", "Left"))) |> pretty_table("Demographics") |>
  tab_footnote("Left: (EHI = -100)  | Right: (EHI = +100) | Mixed: Everyone in between")
```
<br>
<br>

Reaction time is modeled as a linear effect of field, level, and handedness, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field*level*handedness + (1 | subject) )`
<br>
<br>

```{r}
## Make a model with two handedness bins: Right and Left
aah_for_rt_model_2bins_strong <- aah_for_rt_model |> filter(handedness_extremes %in% c("Right", "Left"))
rt_model_2bins_strong <- lmer(rt ~ field*level*handedness_extremes + (1 | subject), data = aah_for_rt_model_2bins_strong)

if (use_cached_model_rt == FALSE) {
  ## Create emmeans model object, and manually cache it.
  rt_emm_2bins_strong <- emmeans(rt_model_2bins_strong, ~ field * level * handedness_extremes)
  ## Todo: run without z-approximation:
  # rt_emm <- emmeans(rt_model, ~ field * level * handedness, pbkrtest.limit = 59851)
  
  ## Manually cache model
  saveRDS(rt_emm_2bins_strong, here(manual_cache_dir, "rt_emm_2bins_strong.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_emm_2bins_strong <- readRDS(here(manual_cache_dir, "rt_emm_2bins_strong.rds"))
}
```

```{r}
## Sanity check: use emmeans() to test 3-way interaction.
rt_interaction_emm <- rt_emm_2bins_strong |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T)

rt_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level by handedness interaction (RT)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means LVF global bias is stronger in right handers (as predicted by AAH)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>

### Within each level (local and global), do right and left handers differ in the effect of field?
```{r}
rt_emm_2bins_strong |> contrast(interaction = "consec", by = c("level")) |> 
  summary(infer = T) |> 
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Interaction of field by handedness, for each level (RT)") |>
  tab_footnote(footnote = "A positive number means more RVF bias for right handers",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>

### Within each level and handedness group, what is the effect of field?

E.g., for local shapes, what is the magnitude of right handers' RVF bias, and left handers' LVF bias?

```{r}
rt_emm_2bins_strong |> contrast("revpairwise", by = c("level", "handedness_extremes")) |> 
  summary(infer = T) |> 
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Effect of field, for each level, for each handedness group (RT)") |>
  tab_footnote(footnote = "A positive number means RVF bias; negative, LVF bias",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>

