---
title: "Action Asymmetry Experiment (n = 1008): Figures for CogSci 2023 submission"
pagetitle: "aah | exp | analysis (shape)"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))
source(here::here("lib", "3c_analyze_shape", "stats.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- here::here("data", "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_4a")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_4a")

use_cached_models <- T

use_cached_figs <- T

if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
}
```

```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all)

#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Code handedness

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("RVF", "LVF")))

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
acc_subject <- aah |> group_by(subject, field, level, handedness) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, handedness, field, level, acc) |>
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")
```

# {.tabset .tabset-pills}

## Demographics

Make tables with all information we would want to report.

## Preregistered 3-way (RT, bins)

Show interaction at each level: 8 boxes, 4 boxes, 2 boxes.

<!-- ## Preregistered 3-way (accuracy, bins) -->

<!-- Show interaction at each level: 8 boxes, 4 boxes, 2 boxes. -->

## Preregistered 3-way (RT, continuous)

<!-- ## Preregistered 3-way (accuracy, continuous) -->

## Zoom: EHI +/- 100

Show 3-way (categorical) for strong left vs. right handers.

<!-- ## Zoom: EHI +/- 100, squares only -->

<!-- Show 3-way (categorical) for strong left vs. right handers, squares only. -->

## Final proposed figures
- Compound figure showing RT interaction (bins; 8, 4, 2)
- Scatterplot-like figure showing RT interaction (continuous)
- Zoom: RT interaction for EHI +/-100



