---
title: "Action Asymmetry Experiment (n = 1008): Figures for CogSci 2023 submission"
pagetitle: "aah | exp | analysis (shape)"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)
library(ggh4x) ## for nested facets

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))
source(here::here("lib", "3c_analyze_shape", "stats.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- here::here("data", "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_4a")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_4a")

use_cached_models <- T

use_cached_figs <- F

if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
}
```

```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all) |>
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 & ehi < 100 ~ "Mixed")
  )


#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long) |>
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 &
                                      ehi < 100 ~ "Mixed")
  ) |> rename(shape = target)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Code handedness

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("RVF", "LVF")))

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
acc_subject <- aah |> group_by(subject, field, level, handedness) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, handedness, field, level, acc) |>
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")
```

# {.tabset .tabset-pills}

## Demographics

Demographic numbers to put in tables or text.

### Everyone

Demographics for all included participants.
```{r demo_summary}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>
```{r demo_race}
demo_race_table(aah_summary) |> pretty_table()
```
<br>
```{r demo_ethnicity}
demo_ethnicity_table(aah_summary) |> pretty_table()
```
<br>

### By handedness group

Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary) |> pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>

## EHI distribution

```{r ehi_distribution_plot}
fig_path_var <- here(fig_dir, "demo_ehi_dots_blue.png")

if (use_cached_rtfigs == F) {
  ehi_plot_data <- aah_summary |> group_by(ehi) |> summarize(n = n())
  g <- gg_ehi_dotarea(ehi_plot_data, plot_color = plot_blue)
  ggsave(fig_path_var, g, "png", height = 3, width = 6)
}

include_graphics(fig_path_var)
```
<br>
<br>
<br>
<br>
```{r ehi_distribution_plot_purple1}
middle_purple1 <- "#996F91" ## In between plot colors one and two
fig_path_var <- here(fig_dir, "demo_ehi_dots_purple.png")

if (use_cached_rtfigs == T) {
  ehi_plot_data <- aah_summary |> group_by(ehi) |> summarize(n = n())
  g <- gg_ehi_dotarea(ehi_plot_data, plot_color = middle_purple1)
  ggsave(fig_path_var, g, "png", height = 3, width = 6)
}

include_graphics(fig_path_var)
```
<br>
<br>
<br>
<br>
```{r ehi_distribution_plot_purple2}
middle_purple2 <- "#886e92" ## In between plot colors one and two
fig_path_var <- here(fig_dir, "demo_ehi_dots_purple2.png")

if (use_cached_rtfigs == T) {
  ehi_plot_data <- aah_summary |> group_by(ehi) |> summarize(n = n())
  g <- gg_ehi_dotarea(ehi_plot_data, plot_color = middle_purple2)
  ggsave(fig_path_var, g, "png", height = 3, width = 6)
}

include_graphics(fig_path_var)
```


## Preregistered 3-way (RT, bins) {.active}

Show interaction at each level: 8 boxes, 4 boxes, 2 boxes.

---

Dots show per-subject means, error bars show SEM.

```{r plot_rt_config}
plot_color <- plot_colors[[5]] # Color for interaction plots with only one color.

# handedness_labeller_40 <- c(
#   Right = "Right handers (EHI >= +40)",
#   Left = "Left handers (EHI <= -40)"
# )
# 
# handedness_labeller_40_short <- c(
#   Right = "Right \n EHI > +40",
#   Left = "Left \n EHI < -40"
# )
# 
# handedness_labeller_generic_short <- c(
#   Right = "Right \n handers",
#   Left = "Left \n handers"
# )
```

```{r plot_rt_1_horizontal}
fig_path_var <- here(fig_dir, "rt_1_horizontal.png")

if (use_cached_rtfigs == FALSE) {
  rt_subject_plot <- rt_subject |>
    filter(handedness %in% c("Left", "Right"))
  
    g <- gg_rt_1_horizontal(title = "Global bias asymmetry by handedness (EHI cut at +/-40)",
                          rt_subject_plot,  plot_colors
    )
    
  ggsave(fig_path_var, g, "png", height = 3, width = 8)
}

include_graphics(fig_path_var)
```

```{r plot_rt_2_horizontal}
fig_path_var <- here(fig_dir, "rt_2_horizontal.png")

if (use_cached_rtfigs == FALSE) {
  rt_subject_plot <- rt_subject |>
    filter(handedness %in% c("Left", "Right"))
  
    g <- gg_rt_2_horizontal(title = "Hemifield bias for global and local targets, by handedness (EHI cut at +/-40)",
                          rt_subject_plot,
                          handedness_labeller = NULL,
                          plot_colors = plot_colors
    )
    
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}

include_graphics(fig_path_var)
```

```{r plot_rt_4_horizontal}
fig_path_var <- here(fig_dir, "rt_4_horizontal.png")

if (use_cached_rtfigs == F) {
  rt_subject_plot <- rt_subject |>
    filter(handedness %in% c("Left", "Right"))
  
    g <- gg_rt_4_horizontal(title = "Reaction time by level, field, and handedness (EHI cut at +/-40)",
                          rt_subject_plot,
                          handedness_labeller = NULL,
                          plot_colors = plot_colors
    )
    
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}

include_graphics(fig_path_var)
```

---

**TODO?**. Show model-estimated mean & CI, instead of per-subject.

<br>

<!-- ## Preregistered 3-way (accuracy, bins) -->

<!-- Show interaction at each level: 8 boxes, 4 boxes, 2 boxes. -->


## Zoom: EHI +/- 100

Show 3-way (categorical) for strong left vs. right handers. Error bars show SEM.

```{r plot_rt_1_horizontal_zoom}
fig_path_var <- here(fig_dir, "rt_1_horizontal_zoom.png")

if (use_cached_rtfigs == FALSE) {
  
  rt_subject_plot <- aah_correct |>
    group_by(subject, field, level, handedness_extremes) |>
    summarize(rt = median(rt)) |>
    filter(handedness_extremes %in% c("Left", "Right")) |>
    rename(handedness = handedness_extremes) |>
    filter(handedness %in% c("Left", "Right"))
  
  g <- gg_rt_1_horizontal(title = "Global bias asymmetry by handedness (EHI = +/-100)",
                          rt_subject_plot, plot_colors
    )
  
  ggsave(fig_path_var, g, "png", height = 3, width = 8)
}

include_graphics(fig_path_var)
```

```{r plot_rt_2_horizontal_zoom}
fig_path_var <- here(fig_dir, "rt_2_horizontal_zoom.png")

if (use_cached_rtfigs == FALSE) {
  
  rt_subject_plot <- aah_correct |>
    group_by(subject, field, level, handedness_extremes) |>
    summarize(rt = median(rt)) |>
    filter(handedness_extremes %in% c("Left", "Right")) |>
    rename(handedness = handedness_extremes) |>
    filter(handedness %in% c("Left", "Right"))
  
    g <- gg_rt_2_horizontal(title = "Hemifield bias for global and local targets, by handedness (EHI = +/-100)",
                          rt_subject_plot,
                          handedness_labeller = NULL,
                          plot_colors = plot_colors
    )
    
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}

include_graphics(fig_path_var)
```

```{r plot_rt_4_horizontal_zoom}
fig_path_var <- here(fig_dir, "rt_4_horizontal_zoom.png")

if (use_cached_rtfigs == F) {
  
  rt_subject_plot <- aah_correct |>
    group_by(subject, field, level, handedness_extremes) |>
    summarize(rt = median(rt)) |>
    filter(handedness_extremes %in% c("Left", "Right")) |>
    rename(handedness = handedness_extremes) |>
    filter(handedness %in% c("Left", "Right"))
  
    g <- gg_rt_4_horizontal(title = "Reaction time by level, field, and handedness (EHI = +/-100)",
                          rt_subject_plot,
                          handedness_labeller = NULL,
                          plot_colors = plot_colors
    )
    
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}

include_graphics(fig_path_var)
```

## Zoom: Shape

Show 3-way (categorical) for strong left vs. right handers, for squares only (and/or squares vs circles). Error bars show SEM.
```{r}
if (use_cached_rtfigs == FALSE) {
  rt_subject_plot_zoom_squares <- aah_correct |>
    filter(shape == "Square") |>
    group_by(subject, field, level, handedness_extremes) |>
    summarize(rt = median(rt)) |>
    filter(handedness_extremes %in% c("Left", "Right")) |>
    rename(handedness = handedness_extremes) |>
    filter(handedness %in% c("Left", "Right"))
}
```

```{r plot_rt_1_horizontal_zoom_squares}
fig_path_var <- here(fig_dir, "rt_1_horizontal_zoom_squares.png")

if (use_cached_rtfigs == FALSE) {
  g <- gg_rt_1_horizontal(
    title = "Global bias asymmetry by handedness (EHI = +/- 100), square targets only",
    rt_subject_plot = rt_subject_plot_zoom_squares,
    plot_colors
    )
  
  ggsave(fig_path_var, g, "png", height = 3, width = 8)
}

include_graphics(fig_path_var)
```

```{r plot_rt_2_horizontal_zoom_squares}
fig_path_var <- here(fig_dir, "rt_2_horizontal_zoom_squares.png")

if (use_cached_rtfigs == F) {
  
  g <- gg_rt_2_horizontal(
      title = "Hemifield bias for global and local targets, by handedness (EHI = +/-100), squares only",
      rt_subject_plot = rt_subject_plot_zoom_squares,
      plot_colors)
    
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}

include_graphics(fig_path_var)
```

```{r plot_rt_4_horizontal_zoom_squares}
fig_path_var <- here(fig_dir, "rt_4_horizontal_zoom_squares.png")

if (use_cached_rtfigs == F) {
  
  rt_subject_plot <- aah_correct |>
    filter(shape == "Square") |> 
    group_by(subject, field, level, handedness_extremes) |>
    summarize(rt = median(rt)) |>
    filter(handedness_extremes %in% c("Left", "Right")) |>
    rename(handedness = handedness_extremes) |>
    filter(handedness %in% c("Left", "Right"))
  
    g <- gg_rt_4_horizontal(
      title = "Hemifield bias for global and local targets, by handedness (EHI = +/-100), squares only",
      rt_subject_plot = rt_subject_plot_zoom_squares,
      plot_colors
    )
    
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}

include_graphics(fig_path_var)
```


<!-- ## Zoom: EHI +/- 100, squares only -->

<!-- Show 3-way (categorical) for strong left vs. right handers, squares only. -->


## Preregistered 3-way (RT, continuous)

<!-- ## Preregistered 3-way (accuracy, continuous) -->

## Discussion

### Questions for discussion

- Should we show SEM/CI from the subject-level data, or from the full mixed model?
- Is it enough to show the "tier one" figures listed below? Should we show any figures illustrating zoom analyses, and the continuous analysis?
- Which figures show the interaction most clearly? Could we just show the 4-box plot?
- Is it worth showing the 8-box data for the main analysis? I think it would be nice to show this raw data.
- Any feedback on the design of the graphs?


### Proposal

#### Tier one
(1) EHI
(2) (a, b, c) Main result: Compound figure showing RT interaction (1-box, 4-box, 8-box) in full sample.

#### Tier two (could leave out if we need the space)
(3) (a, b) Zoom: compound figure showing effect of shape, within strong lefties (1-box, 4-box). This shows the stro
(4) Scatterplot-like figure showing RT interaction (continuous) [If convincing]

### Brainstorm - all figures I think might be worth showing
- EHI
- (a, b, c) Main result: Compound figure showing RT interaction (1-box, 4-box, 8-box) in full sample.
- (a, b) Zoom: Compound figure showing RT interaction (1-box, 4-box) in strong handers, or strong handers with squares only.
- (a, b) Zoom: show effect of shape (1-box, 4-box),  either in strong handers only (revealing largest effect size, and also illustrating the effect of shape), or in the full sample (focusing on the effect of shape itself)
- Scatterplot-like figure showing RT interaction (continuous)





