---
title: "Action Asymmetry Experiment (n = 1008): Figures for CogSci 2023 submission"
pagetitle: "aah | exp | analysis (shape)"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)
library(ggh4x) ## for nested facets

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots.R"))
source(here::here("lib", "3c_analyze_shape", "stats.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- here::here("data", "proc_exp_n1008")
fig_dir <- here::here("figures", "exp_n1008_4a")
manual_cache_dir <- here::here("manual_cache", "exp_n1008_4a")

use_cached_models <- T

use_cached_figs <- F

if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
}
```

```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all) |>
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 & ehi < 100 ~ "Mixed")
  )


#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long) |>
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 &
                                      ehi < 100 ~ "Mixed")
  )

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Code handedness

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("RVF", "LVF")))

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))

## Prepare subject-level LVF Global bias summary (RT)
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
acc_subject <- aah |> group_by(subject, field, level, handedness) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, handedness, field, level, acc) |>
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")
```

# {.tabset .tabset-pills}

## Demographics

### Everyone

Demographics for all included participants.
```{r demo_summary}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>
```{r demo_race}
demo_race_table(aah_summary) |> pretty_table()
```
<br>
```{r demo_ethnicity}
demo_ethnicity_table(aah_summary) |> pretty_table()
```
<br>

### By handedness group {.active}

Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary) |> pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>
```{r demo_plot_ehi_binned}
plot_color = plot_blue
fig_path <- here(fig_dir, "demo_ehi_binned.png")

aah_summary |> group_by(ehi) |> summarize(n = n())

if (use_cached_demofigs == FALSE) {
g <- ggplot(aah_summary, aes(x = ehi)) +
  geom_histogram(color = NA, fill = plot_color, alpha = .8, binwidth = 10, boundary = 100) +
  # geom_vline(xintercept = -92, color = plot_colors[[2]]) +
  # geom_vline(xintercept = 92, color = plot_colors[[2]]) +
  geom_vline(xintercept = -40, color = "gray50") +
  geom_vline(xintercept = 40, color = "gray50") +
  scale_x_continuous(breaks = c(-100, -40, 0, 40, 100),
                     minor_breaks = seq(-100, 100, 20)) +
  # scale_x_continuous(breaks = c(-100, -40, 0, 40, 100),
  #                    minor_breaks = seq(-100, 100, 20)) +
  labs(x = "Edinburgh Handedness Inventory (EHI) laterality quotient",
       y = "Number of participants",
       title = "Hand preference distribution")

g <- g |> gg_style() |> gg_style_demo() + theme(aspect.ratio = 1/2)

g
ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
g
```

```{r ehi_distribution_plot}
## Show dots instead of bars
ehi_plot_data <- aah_summary |> group_by(ehi) |> summarize(n = n())
ehi_plot_data
ehi_n_leftest <- ehi_plot_data |> filter(ehi == -100) |> pull(n)
ehi_n_rightest <- ehi_plot_data |> filter(ehi == 100) |> pull(n)

fig_path <- here(fig_dir, "demo_ehi_dots.png")

line_color = plot_color


if (use_cached_demofigs == FALSE) {
g <- ggplot(ehi_plot_data, aes(x = ehi, y = n)) +
  # geom_col(width = 1, fill = plot_color) +
  geom_vline(xintercept = -40, color = "gray50") +
  geom_vline(xintercept = 40, color = "gray50") +
  geom_area(fill = plot_color, alpha = .5, color = NA, linewidth = 0) +
  geom_line(color = line_color, linewidth = .5) +
  # geom_segment(x = -100, xend = -100, y = 0, yend = ehi_n_leftest, color = line_color, linewidth = .5, alpha = .5) +
  # geom_segment(x = 100, xend = 100, y = 0, yend = ehi_n_rightest, color = line_color, linewidth = .5) +
  geom_point(fill = plot_color, shape = 21, size = 3) +
  # geom_histogram(color = NA, fill = plot_color, alpha = .8, binwidth = 10, boundary = 100) +
  # geom_vline(xintercept = -92, color = plot_colors[[2]]) +
  # geom_vline(xintercept = 92, color = plot_colors[[2]]) +
  scale_x_continuous(breaks = c(-100, -75, -50, -25, 0, 25, 50, 75, 100),
                     minor_breaks = seq(-100, 100, 12.5),
                     expand = expansion(mult = c(.025, .025))) +
  scale_y_continuous(expand = expansion(mult = c(0, .1))) +
  # scale_x_continuous(breaks = c(-100, -40, 0, 40, 100),
  #                    minor_breaks = seq(-100, 100, 20)) +
  labs(x = "Laterality quotient from 4-item Veale Edinburgh Handedness Inventory (EHI)",
       y = "Number of participants",
       title = "Hand preference distribution")

g <- g + theme_minimal(base_size = 10) +
    theme(aspect.ratio = 1 / 2,
          plot.title = element_text(margin = margin(b = 10, unit = "pt"),
                                    hjust = .5),
          axis.ticks.x = element_blank(),
          axis.title.x = element_text(margin = margin(t = 5, unit = "pt")),
          axis.ticks.y = element_blank(),
          axis.title.y = element_text(margin = margin(r = 5, unit = "pt"))
    )

ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
g
```

```{r ehi_distribution_plot_hacky}
## Show dots instead of bars
ehi_plot_data <- aah_summary |> group_by(ehi) |> summarize(n = n())
ehi_plot_data
ehi_n_leftest <- ehi_plot_data |> filter(ehi == -100) |> pull(n)
ehi_n_rightest <- ehi_plot_data |> filter(ehi == 100) |> pull(n)

fig_path <- here(fig_dir, "demo_ehi_dots.png")

line_color = plot_color
yr <- ehi_plot_data$n
xr <- ehi_plot_data$ehi

y_breaks = c(0, 50, 100, 150, 200)
x_breaks = seq(-100, 100, 25)


xr
x_breaks
pretty(xr)
xr <- pretty(xr)



if (use_cached_demofigs == FALSE) {
g <- ggplot(ehi_plot_data, aes(x = ehi, y = n)) +

  ### Define vertical lines: y axis and panel.major/minor.y
  geom_segment(aes(
    ## y = rep(9, 16) = [9, 9, 9, 9, 9, 9, 9, 9, 9, 9, 9, 9, 9, 9, 9, 9]
    y = rep(0, length(xr)),
    ## yend = rep(182, 16) = [182, 182...]
    yend = rep(200, length(xr)),
    ## x = [-100, -87.5, -75, ...]
    x = xr,
    ## xend = [-100, -87.5, -75, ...]
    xend = xr
  ), colour = "gray50") +

  ### Define horizontal lines: x axis and panel.major/minor.x
  geom_segment(aes(
    x = rep(min(xr), length(yr)),
    xend = rep(max(xr), length(yr)),
    y = yr,
    yend = yr
  ), colour = "gray50") +
  
  
  # geom_vline(xintercept = -40, color = "gray50") +
  # geom_vline(xintercept = 40, color = "gray50") +
  # geom_area(fill = plot_color, alpha = .5, color = NA, linewidth = 0) +
  geom_line(color = line_color, linewidth = .5) +
  
  
  # geom_segment(x = -100, xend = -100, y = 0, yend = ehi_n_leftest, color = line_color, linewidth = .5, alpha = .5) +
  # geom_segment(x = 100, xend = 100, y = 0, yend = ehi_n_rightest, color = line_color, linewidth = .5) +
  geom_point(fill = plot_color, shape = 21, size = 3) +
  
  scale_x_continuous(breaks = x_breaks,
                     # minor_breaks = seq(-100, 100, 12.5),
                     expand = c(0,0.02*diff(range(ehi_plot_data$n)))
                     ) +
                     # expand = expansion(mult = c(.025, .025))) +
  scale_y_continuous(breaks = y_breaks,
                     expand = c(0,0.02*diff(range(ehi_plot_data$ehi)))
                     ) +
  
  
  # scale_y_continuous(breaks = yr, expand = c(0,0.01*diff(range(ehi_plot_data$n)))) +
  # scale_x_continuous(breaks = xr, expand = c(0,0.02*diff(range(ehi_plot_data$ehi)))) +
  theme_classic() +
  theme(axis.line = element_blank()) +
  
  
  labs(x = "4-item Veale Edinburgh Handedness Inventory (EHI) laterality quotient",
       y = "Number of participants",
       title = "Hand preference distribution")

g <- g + theme(aspect.ratio = 1/2, axis.ticks.x = element_blank(), axis.ticks.y = element_blank())
# g <- g + theme_minimal()
# g <- g |> gg_style()
# g <- g + theme_minimal(base_size = 10) +
#     theme(aspect.ratio = 1 / 2,
#           axis.ticks.x = element_blank()
#     )
# g <- g |> gg_style() + theme_minimal()
# g <- g |> gg_style() |> gg_style_demo() +theme_classic()+ theme(aspect.ratio = 1/2, axis.line = element_blank())

g
ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
g
```

```{r ehi_plot_manual_axes}
y_breaks <- pretty(ehi_plot_data$n)
x_breaks <- pretty(ehi_plot_data$ehi)

y_breaks = c(0, 50, 100, 150, 200)
x_breaks = seq(-100, 100, 25)


ggplot(data = ehi_plot_data) +
  
  ## vertical lines (major)
  # geom_segment(aes(
  #   y = rep(min(y_breaks), length(x_breaks)),
  #   yend = rep(max(y_breaks), length(x_breaks)),
  #   x = x_breaks,
  #   xend = x_breaks
  # ), colour = "gray50") +
  # 
  # ## horizontal lines (major)
  # geom_segment(aes(
  #   x = rep(min(x_breaks), length(y_breaks)),
  #   xend = rep(max(x_breaks), length(y_breaks)),
  #   y = y_breaks,
  #   yend = y_breaks
  # ), colour = "gray50") +
  
  geom_line(aes(ehi, n), color = line_color, linewidth = .5) +
  geom_area(aes(ehi, n), fill = plot_color, alpha = .5, color = NA, linewidth = 0) +
  geom_point(data = ehi_plot_data, aes(ehi, n), size = 4, shape = 21, fill = plot_color) +
  
  # geom_point(fill = plot_color, shape = 21, size = 3) +
  scale_y_continuous(breaks = y_breaks,
                     expand = c(0, 0.02 * diff(range(ehi_plot_data$ehi)))) +
  scale_x_continuous(breaks = x_breaks,
                     expand = c(0, 0.02 * diff(range(ehi_plot_data$n)))) +
  theme_classic() +
  theme(axis.line = element_blank()) +
  labs(x = "4-item Veale Edinburgh Handedness Inventory (EHI) laterality quotient",
       y = "Number of participants",
       title = "Hand preference distribution") +
  theme(axis.title.x = element_text(margin = margin(t = 10, unit = "pt"))) +
  theme(aspect.ratio = 1/2, axis.ticks.x = element_blank(), axis.ticks.y = element_blank())
```

## Preregistered 3-way (RT, bins)

Show interaction at each level: 8 boxes, 4 boxes, 2 boxes.

<!-- ## Preregistered 3-way (accuracy, bins) -->

<!-- Show interaction at each level: 8 boxes, 4 boxes, 2 boxes. -->

## Preregistered 3-way (RT, continuous)

<!-- ## Preregistered 3-way (accuracy, continuous) -->

## Zoom: EHI +/- 100

Show 3-way (categorical) for strong left vs. right handers.

<!-- ## Zoom: EHI +/- 100, squares only -->

<!-- Show 3-way (categorical) for strong left vs. right handers, squares only. -->

## Final proposed figures
- Compound figure showing RT interaction (bins; 8, 4, 2)
- Scatterplot-like figure showing RT interaction (continuous)
- Zoom: RT interaction for EHI +/-100



