---
title: "Power analysis for preregistration"
pagetitle: "aah | pilot | power analysis"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
# library(broom)
library(gt)

# library(ggpubr) ## functions for plotting SD, SEM, CI.
# library(ggbeeswarm)
# library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
```

```{r config}
data_dir <- here::here("data")
proc_dir <- here::here(data_dir, "proc_pilot")
cache_dir <- here::here("manual_cache", "pilot")

## TODO: specify cache for models from each script version:
## pilot, main experiment 
## (Each will have its own "rt_emm.rds", for example)

use_cached_model_rt <- TRUE
use_cached_model_acc <- TRUE
use_cached_model_rt_ehi <- TRUE
use_cached_model_acc_ehi <- TRUE
```

```{r load_and_prep_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)

#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all)

#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))
```

# {.tabset}

## Demographics
```{r demo_summary}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```

## Estimate: Field x Level {.tabset .tabset-pills .active}
Estimate the effect size of the field x level interaction seen in right handers.
<br>
<br>

### Reaction time

Reaction time is modeled as a linear effect of field and level, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field + level + field:level + (1 | subject) )`
<br>
<br>

```{r rt_model}
## Make a linear model using data from every trial.
## Fixed effects: field, level (and their interaction)
## Random effects: subject.
## rt ~ field + level + field:level + (1 | subject)
rt_model <- lmer(rt ~ field:level + field + level + (1 | subject), data = aah_for_rt_model)

if (use_cached_model_rt == FALSE) {
  ## Create emmeans model object, and manually cache it.
  rt_emm <- emmeans(rt_model, ~ field * level, pbkrtest = 13184)
  
  ## Manually cache model
  saveRDS(rt_emm, here(cache_dir, "rt_emm.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_emm <- readRDS(here("manual_cache", "rt_emm.rds"))
}
```

```{r rt_interaction_emm}
## Use emmeans() to test 2-way interaction.
rt_interaction_emm <- rt_emm |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T)
#rt_interaction_emm

rt_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (RT)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means global bias is stronger in LVF (as predicted for right handers)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = lower.CL)) |>
  tab_footnote(footnote = "Degrees-of-freedom method: kenward-roger",
               locations = cells_column_labels(columns = df))
```

### Accuracy
Accuracy is modeled as a binomial effect of field and level, using binary correct/incorrect data from every target-present trial:
<br>
<br>
`glmer( correct ~ field + level + field:level + (1 | subject), family = "binomial" )`
<br>
<br>
```{r acc_model}
## Make a binomial logistic model using data from every trial.
## Fixed effects: field, level (and their interaction)
## Random effects: subject.
## correct ~ field + level + field:level + (1 | subject)
acc_model <- glmer(correct ~ field:level + field + level + (1 | subject),
                   data = aah,
                   family = "binomial")

if (use_cached_model_acc == FALSE) {
  ## Create emmeans model object, and manually cache it.
  acc_emm <- emmeans(acc_model, ~ field * level)
  
  ## Manually cache model
  saveRDS(acc_emm, here("manual_cache", "acc_emm.rds"))
  
} else if (use_cached_model_acc == TRUE) {
  ## Load cached model
  acc_emm <- readRDS(here("manual_cache", "acc_emm.rds"))
}
```


```{r acc_interaction_emm}
## Is there an interaction of field x level?
## Use an emmeans contrast
acc_interaction_emm <- acc_emm |>
  contrast(interaction = c("consec")) |>
  summary(infer = T, type = "response")
#acc_interaction_emm

acc_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio > 1 means global bias is stronger in the LVF, as predicted for right handers.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "I don't understand why df is 'Inf' here, but I think it is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = asymp.LCL)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```

