---
title: "Power analysis for preregistration: Accuracy"
pagetitle: "aah | pilot | power (acc)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
# library(broom)
library(gt)

library(simr) # for power analyses

# library(ggpubr) ## functions for plotting SD, SEM, CI.
# library(ggbeeswarm)
# library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
```

```{r config}
data_dir <- here::here("data")
proc_dir <- here::here(data_dir, "proc_pilot")
cache_dir <- here::here("manual_cache", "pilot")

## TODO: specify cache for models from each script version:
## pilot, main experiment 
## (Each will have its own "rt_emm.rds", for example)

use_cached_model_rt <- TRUE
use_cached_model_acc <- TRUE
use_cached_model_rt_ehi <- TRUE
use_cached_model_acc_ehi <- TRUE

use_cached_sims <- FALSE


# use_cached_model_rt <- FALSE
# use_cached_model_acc <- FALSE
# use_cached_model_rt_ehi <- FALSE
# use_cached_model_acc_ehi <- FALSE
```

```{r simr_config}
n_sim <- 1000
n_sim_acc <- 100
```

```{r load_and_prep_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)

#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES
aah_summary <- filter_aah_summary_for_analysis(aah_summary_all)

#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
aah <- filter_aah_long_for_analysis(aah_long)

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
aah_correct <- aah |> filter(correct == T)
## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Local", "Global")),
         field = field |> factor(levels = c("RVF", "LVF")))
```

# {.tabset}

## Demographics
```{r demo_summary}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```

## Estimate: Field x Level {.tabset .tabset-pills}
Estimate the effect size of the field x level interaction seen in right handers.
<br>
<br>

### Reaction time

Reaction time is modeled as a linear effect of field and level, using data from every target-present trial with a "go" response:
<br>
<br>
`lmer( rt ~ field + level + field:level + (1 | subject) )`
<br>
<br>

```{r rt_model}
## Make a linear model using data from every trial.
## Fixed effects: field, level (and their interaction)
## Random effects: subject.
## rt ~ field + level + field:level + (1 | subject)
rt_model <- lmer(rt ~ field:level + field + level + (1 | subject), data = aah_for_rt_model)

if (use_cached_model_rt == FALSE) {
  ## Create emmeans model object, and manually cache it.
  rt_emm <- emmeans(rt_model, ~ field * level, pbkrtest = 13184)
  
  ## Manually cache model
  saveRDS(rt_emm, here(cache_dir, "rt_emm.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_emm <- readRDS(here(cache_dir, "rt_emm.rds"))
}
```

```{r rt_interaction_emm}
## Use emmeans() to test 2-way interaction.
rt_interaction_emm <- rt_emm |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T)
#rt_interaction_emm

rt_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (RT)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means global bias is stronger in LVF (as predicted for right handers)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = lower.CL)) |>
  tab_footnote(footnote = "Degrees-of-freedom method: kenward-roger",
               locations = cells_column_labels(columns = df))
```

### Accuracy
Accuracy is modeled as a binomial effect of field and level, using binary correct/incorrect data from every target-present trial:
<br>
<br>
`glmer( correct ~ field + level + field:level + (1 | subject), family = "binomial" )`
<br>
<br>
```{r acc_model}
## Make a binomial logistic model using data from every trial.
## Fixed effects: field, level (and their interaction)
## Random effects: subject.
## correct ~ field + level + field:level + (1 | subject)

if (use_cached_model_acc == FALSE) {
  ## Create model object
  acc_model <- glmer(correct ~ field:level + field + level + (1 | subject),
                   data = aah_for_acc_model,
                   family = "binomial")
  
  ## Create emmeans model object
  acc_emm <- emmeans(acc_model, ~ field * level)
  
  ## Manually cache model, emmeans object
  saveRDS(acc_emm, here(cache_dir, "acc_emm.rds"))
  saveRDS(acc_model, here(cache_dir, "acc_model.rds"))
  
} else if (use_cached_model_acc == TRUE) {
  ## Load cached model
  acc_model <- readRDS(here(cache_dir, "acc_model.rds"))
  acc_emm <- readRDS(here(cache_dir, "acc_emm.rds"))
}
```


```{r acc_interaction_emm}
## Is there an interaction of field x level?
## Use an emmeans contrast
acc_interaction_emm <- acc_emm |>
  contrast(interaction = c("consec")) |>
  summary(infer = T, type = "response")
#acc_interaction_emm

acc_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio > 1 means global bias is stronger in the LVF, as predicted for right handers.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "I don't understand why df is 'Inf' here, but I think it is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = asymp.LCL)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```

```{r}
acc_interaction_emm <- acc_emm |>
  contrast(interaction = c("consec")) |>
  summary(infer = T)
#acc_interaction_emm

acc_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Log odds ratio",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "I don't understand why df is 'Inf' here, but I think it is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = asymp.LCL)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```


## Power: Binned handedness {.tabset .tabset-pills .active}
### Reaction time

```{r simulate_lefties_rt_bin}
rt_model <- lmer(rt ~ field:level + field + level + (1 | subject), data = aah_for_rt_model)
## Right handers' field x level effect is 28.74ms, SE 7.60.

if (use_cached_sims == FALSE) {
  ## Create simulation(s), and manually cache.
  
  ## Create simulated data with left handers,
  ## and a binary handedness variable.
  ## Lefty handedness can be simulated as the
  ## mirror image of right handers' EHI scores.
  
  ## Then, we can estimate the effect of the difference btw handedness groups.
  rt_data_pilot <- aah_for_rt_model
  
  ## Make simulated lefties with the same RT data as righties:
  rt_sim_lefties <- rt_data_pilot |> mutate(ehi = -ehi)
  
  ## Make a dataset that includes the simulated lefties.
  rt_sim <- add_row(rt_data_pilot, rt_sim_lefties) |>
    mutate(handedness = case_when(ehi > 0 ~ "right",
                                  ehi <= 0 ~ "left"))
  
  ## Make a model using the simulated data
  rt_model_sim <-
    lmer(rt ~ field * level * handedness + (1 |
                                              subject), data = rt_sim)
  
  ## Manually cache dataset and model
  saveRDS(rt_sim, here(cache_dir, "rt_sim.rds"))
  saveRDS(rt_model_sim, here(cache_dir, "rt_model_sim.rds"))
  
} else if (use_cached_sims == TRUE) {
  ## Load cached model
  rt_sim <- readRDS(here(cache_dir, "rt_sim.rds"))
  rt_model_sim <- readRDS(here(cache_dir, "rt_model_sim.rds"))
}

#rt_model_sim |> summary()
## As expected, 
## right handers' field x level effect is 28.74ms, SE 7.60.
```

Calculate power to detect an interaction if lefties' LVF Global bias is 14.37ms or lower (1/2 the effect we saw in our pilot righties).
```{r rt_14.37ms_n103_bin}
## Modify the estimated interaction of field*level*handedness:
## If the effect is 1/2x in left handers (14.37ms difference)
fixef(rt_model_sim)["fieldLVF:levelLocal:handednessright"] <- 14.37
#rt_model_sim |> summary()

## Now, we have a simulated model in which left handers' 
## interaction effect is 1/2x right handers.
## With 103 subjects, how much power do we have to detect the 3-way interaction effect?
#p1 <- powerSim(rt_model_sim, nsim = n_sim, test = compare(rt ~ field*level + (1 | subject)))
#p1
## nsim = 10, 47% power. nrow = 24946 
## (each 103 subjects have 12,463 rows - 206 have 24946.)

if (use_cached_sims == FALSE) {
  ## Make a model with a large number of subjects, that will hopefully have more than enough power.
  rt_model_sim_extended <-
    extend(rt_model_sim, along = "subject", n = 824)
  #p2 <- powerSim(rt_model_sim_2, nsim = n_sim, test = compare(rt ~ field*level + (1 | subject)))
  ## nsim = 10, 100% power. nrow = 199568 (24946*4)
  
  ## Then, make a power curve using that model as an upper bound.
  rt_pc <- powerCurve(
    fit = rt_model_sim_extended,
    test = compare(rt ~ field * level + (1 |
                                           subject)),
    alpha = 0.05,
    along = "subject",
    breaks = seq(206, 824, 50),
    nsim = n_sim,
  )
  
  saveRDS(rt_model_sim_extended,
          here(cache_dir, "rt_model_sim_extended.rds"))
  saveRDS(rt_pc, here(cache_dir, "rt_model_sim_extended_pc.rds"))
} else if (use_cached_sims == TRUE) {
  rt_pc <- readRDS(here(cache_dir, "rt_model_sim_extended_pc.rds"))
}

rt_pc_tbl <- rt_pc |> summary() |> as_tibble() |>
  rename(
    n_trials = nrow,
    n_subjects = nlevels,
    simulations = trials,
    power = mean
  )
rt_pc_tbl |>
  pretty_table() |> tab_header(title = "Power to detect field x level x handedness (binary) interaction", subtitle =  "alpha =  .05") |>
  tab_footnote(footnote = "Total subjects: 1/2 right, 1/2 left handed.",
               locations = cells_column_labels(columns = n_subjects)) |>
  tab_footnote(footnote = "Number of simulations where the interaction was significant.",
               locations = cells_column_labels(columns = successes)
  )
  
```


### Accuracy

```{r simulate_lefties_acc_bin}
# acc_model |> summary()
# acc_interaction_emm <- acc_emm |>
#   contrast(interaction = c("consec")) |>
#   summary(infer = T, type = "response")
# acc_interaction_emm
## The logodds estimate for the field x level interaction is: 0.484 (OR: 1.62)

if (use_cached_sims == FALSE) {
  ## Create simulation(s), and manually cache.
  
  ## Create simulated data with left handers,
  ## and a binary handedness variable.
  ## Lefty handedness can be simulated as the
  ## mirror image of right handers' EHI scores.
  
  ## Then, we can estimate the effect of the difference btw handedness groups.
  acc_data_pilot <- aah_for_acc_model
  
  ## Make simulated lefties with the same RT data as righties:
  acc_sim_lefties <- acc_data_pilot |> mutate(ehi = -ehi)
  
  ## Make a dataset that includes the simulated lefties.
  acc_sim <- add_row(acc_data_pilot, acc_sim_lefties) |>
    mutate(handedness = case_when(ehi > 0 ~ "right",
                                  ehi <= 0 ~ "left"))
  
  ## Make a model using the simulated data
  acc_model_sim <-
    glmer(correct ~ field * level * handedness + (1|subject), 
          data = acc_sim,
          family = "binomial")
  
  ## Manually cache dataset and model
  saveRDS(acc_sim, here(cache_dir, "acc_sim.rds"))
  saveRDS(acc_model_sim, here(cache_dir, "acc_model_sim.rds"))
  
} else if (use_cached_sims == TRUE) {
  ## Load cached model
  acc_sim <- readRDS(here(cache_dir, "acc_sim.rds"))
  acc_model_sim <- readRDS(here(cache_dir, "acc_model_sim.rds"))
}

#acc_model_sim |> summary()
## As expected, 
## right handers' field x level effect is .484, SE .162
```

Calculate power to detect an interaction if lefties' LVF Global bias is .242 (logodds) or more negative (1/2 the effect we saw in our pilot righties).
```{r acc_242_n103_bin}
## Modify the estimated interaction of field*level*handedness:
# .484 |> exp(). OR: 1.62
# .484/2
# .242 |> exp().  OR: 1.27
## If the effect is 1/2x in left handers (logodds = .242)
acc_model_sim |> summary()
#fixef(acc_model_sim)["fieldLVF:levelGlobal:handednessright"]
fixef(acc_model_sim)["fieldLVF:levelGlobal:handednessright"] <- .242
#acc_model_sim |> summary()

## Now, we have a simulated model in which left handers' 
## interaction effect is 1/2x right handers.

if (use_cached_sims == FALSE) {
  ## Make a model with a large number of subjects, that will hopefully have more than enough power.
  acc_model_sim_extended <-
    extend(acc_model_sim, along = "subject", n = 824)
  #p2 <- powerSim(acc_model_sim_2, nsim = n_sim, test = compare(rt ~ field*level + (1 | subject)))
  ## nsim = 10, 100% power. nrow = 199568 (24946*4)
  
  ## Then, make a power curve using that model as an upper bound.
  acc_pc <- powerCurve(
    fit = acc_model_sim_extended,
    test = compare(correct ~ field * level + (1 |
                                           subject)),
    alpha = 0.05,
    along = "subject",
    breaks = seq(206, 824, 50),
    nsim = n_sim_acc,
  )
  
  saveRDS(acc_model_sim_extended,
          here(cache_dir, "acc_model_sim_extended.rds"))
  saveRDS(acc_pc, here(cache_dir, "acc_model_sim_extended_pc.rds"))
} else if (use_cached_sims == TRUE) {
  acc_pc <- readRDS(here(cache_dir, "acc_model_sim_extended_pc.rds"))
}

acc_pc_tbl <- acc_pc |> summary() |> as_tibble() |>
  rename(
    n_trials = nrow,
    n_subjects = nlevels,
    simulations = trials,
    power = mean
  )
acc_pc_tbl |>
  pretty_table() |> tab_header(title = "Power to detect field x level x handedness (binary) interaction", subtitle =  "alpha =  .05") |>
  tab_footnote(footnote = "Total subjects: 1/2 right, 1/2 left handed.",
               locations = cells_column_labels(columns = n_subjects)) |>
  tab_footnote(footnote = "Number of simulations where the interaction was significant.",
               locations = cells_column_labels(columns = successes))
```


## Power analyses: Continuous handedness {.tabset .tabset-pills}
### Reaction time
In progress.

### Accuracy
In progress.
