---
title: "Action Asymmetry Pilot: Analyses"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)

library(knitr) # For include_graphics

source(here::here("lib", "load_process", "load_process.R"))
source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))

## Todo: put these in a separate file.
## Functions to style plots
gg_style <- function(g) {
  g_styled <- g +
    theme_minimal(base_size = 10) +
    theme(aspect.ratio = 1 / 1,
          axis.ticks.x = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(fill = NA)
    )
    return(g_styled)
}

gg_style_demo <- function(g) {
  g_styled <- g +
    theme_minimal(base_size = 8) +
    theme(aspect.ratio = 1 / 1,
          axis.ticks.x = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(fill = NA, color = "gray50")
    )
    return(g_styled)
}

gg_style_means <- function(g) {
  g_styled <- g +
  theme_minimal() +
  theme(
    aspect.ratio = 2 / 1,
    plot.title = element_text(hjust = 0.5),
    axis.title.x = element_blank(),
    panel.border = element_rect(fill = NA, color = "gray50")
  )
    return(g_styled)
}

plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")

gg_color <- function(g, plot_colors) {
  if (missing(plot_colors)) {
    # By default, use colorblind-safe categorical palette
    plot_colors <- c("#4477AA", "#EE6677", "#CCBB44", "#66CCEE",
                     "#AA3377", "#228833", "#BBBBBB")
  }
  g_colored <- g +
    scale_color_manual(values = plot_colors) +
    scale_fill_manual(values = plot_colors)
  return(g_colored)
}
```

```{r config}
data_dir <- here::here("data")
proc_dir <- here::here(data_dir, "proc_pilot")
fig_dir <- here::here("figures")

use_cached_model_rt <- TRUE
use_cached_model_acc <- TRUE

use_cached_figs <- TRUE


if (use_cached_figs == TRUE) {
  use_cached_demofigs <- TRUE
  use_cached_rtfigs <- TRUE
  use_cached_accfigs <- TRUE
} else if (use_cached_figs == FALSE) {
  use_cached_demofigs <- FALSE
  use_cached_rtfigs <- FALSE
  use_cached_accfigs <- FALSE
}
```

# {.tabset}
```{r load_data}
## Load long data table, and filter out excluded subjects
aah <- readr::read_tsv(
  here(proc_dir, "aah_long.tsv"),
  col_types = cols(
    subject = col_character(),
    block_response = col_character(),
    target = col_character(),
    level = col_character(),
    field = col_character(),
    correct = col_logical(),
    rt = col_double(),
    first_block = col_character(),
    ehi_total = col_double(),
    age = col_double(),
    country = col_character(),
    sex = col_character(),
    education = col_double(),
    race = col_character(),
    hispanic_ethnicity = col_character(),
    rt_overall = col_double(),
    duration_s = col_double(),
    task_experience_response = col_character(),
    task_experience_other_response = col_logical(),
    open_ended_feedback_response = col_character(),
    exclude_many_gos = col_logical(),
    exclude_low_acc = col_logical(),
    exclude_low_rt = col_logical(),
    exclude_high_rt = col_logical(),
    exclude_country = col_logical(),
    exclude_age = col_logical(),
    exclude_done_before = col_logical(),
    exclude_no_ehi = col_logical(),
    exclude = col_logical()
  )
) |>
  filter(exclude == 0) |> 
  select(-starts_with("exclude"))

aah_summary <- readr::read_tsv(
  here(proc_dir, "aah_summary.tsv"),
  col_types = cols(
    subject = col_character(),
    first_block = col_character(),
    ehi_total = col_double(),
    age = col_double(),
    country = col_character(),
    sex = col_character(),
    education = col_double(),
    race = col_character(),
    hispanic_ethnicity = col_character(),
    rt_overall = col_double(),
    duration_s = col_double(),
    task_experience_response = col_character(),
    task_experience_other_response = col_logical(),
    open_ended_feedback_response = col_character(),
    exclude_many_gos = col_double(),
    exclude_low_acc = col_double(),
    exclude_low_rt = col_double(),
    exclude_high_rt = col_double(),
    exclude_country = col_double(),
    exclude_age = col_double(),
    exclude_done_before = col_double(),
    exclude_no_ehi = col_double(),
    exclude = col_double()
  )
) |> 
  filter(exclude == 0) |> 
  select(-starts_with("exclude"))
```

## Demographics
```{r demo_summary}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>
```{r demo_plot_config}
plot_color = plot_blue
```

```{r demo_plot_ehi}
fig_path <- here(fig_dir, "demo_ehi.png")

if (use_cached_demofigs == FALSE) {
g <- ggplot(aah_summary, aes(x = ehi_total)) +
  geom_histogram(color = NA, fill = plot_color, alpha = .8, binwidth = 8, boundary = 100) +
  labs(x = "EHI")+
  xlim(c(-104, 104))

g <- g |> gg_style_demo() + theme(aspect.ratio = 1/2,
                            axis.title.y = element_blank())

ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
```

```{r demo_plot_age}
fig_path <- here(fig_dir, "demo_age.png")

if (use_cached_demofigs == FALSE) {
g <- ggplot(aah_summary, aes(x = age)) +
  geom_histogram(color = NA, fill = plot_color, alpha = .8, binwidth = 1) +
  labs(x = "Age (years)")

g <- g |> gg_style_demo() + theme(aspect.ratio = 1/2,
                            axis.title.y = element_blank())

ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
```

```{r demo_plot_edu}
fig_path <- here(fig_dir, "demo_edu.png")

if (use_cached_demofigs == FALSE) {
g <- ggplot(aah_summary, aes(x = education)) +
  geom_histogram(color = NA, fill = plot_color, alpha = .8, binwidth = 1) +
  labs(x = "Education (years)")

g <- g |> gg_style_demo() + theme(aspect.ratio = 1/2,
                            axis.title.y = element_blank(),
                            axis.text.y = element_blank())

ggsave(fig_path, g, "png", height = 2, width = 4)
}

include_graphics(fig_path)
```
<br>
```{r demo_race}
demo_race_table(aah_summary) |> pretty_table()
```
<br>
```{r demo_ethnicity}
demo_ethnicity_table(aah_summary) |> pretty_table()
```
<br>


## Field x Level {.tabset .tabset-pills .active}
In our pilot sample of right handers, do we see the typical field x level interaction? That is, do participants show a relative bias for global shapes in the left visual field (LVF)?
<br>

### Reaction time
```{r filter_data_to_correct_trials_only}
## Prepare dataset with only correct trials.
aah_correct <- aah |> filter(correct == T) |> 
  mutate(level = recode(level, global = "Global", local = "Local"))
```
#### Plots
```{r plot_rt_config}
plot_color <- plot_colors[[5]] # Color for interaction plots with only one color.
```

```{r plot_rt_4a_all_trials}
## Plot data from every trial, with overall mean, median and bounds.
fig_path_rt_4a <- here(fig_dir, "rt_4a.png")

if (use_cached_rtfigs == FALSE) {
rt_descriptive <- aah_correct |>
  group_by(field, level) |>
  summarize(
    median = median(rt),
    mean = mean(rt),
    SE = sd(rt) / sqrt(length((rt)))
  )

## Facet by: Visual field
g <- ggplot(aah_correct, aes(
  x = level,
  y = rt,
  fill = level,
  color = level
)) +
  geom_quasirandom(alpha = .05, show.legend = F) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .3,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(data = rt_descriptive, aes(y = mean), color = "black", shape = 21,
             show.legend = F) +
  scale_y_continuous(minor_breaks = seq(0 , 2000, 100),
                     breaks = seq(0, 2000, 200)) +
  facet_wrap(~ field) +
  labs(title = "All trials (RT)", x = "Level", y = "Reaction time (ms)")

g <- g |> gg_style_means() |> gg_color()
ggsave(fig_path_rt_4a, g, "png", height = 4, width = 4)
g_rt_4a <- g
}

#include_graphics(fig_path_g_rt_4a)
```
```{r plot_rt_4}
fig_path_rt_4 <- here(fig_dir, "rt_4.png")

if (use_cached_rtfigs == FALSE) {
rt_subject <- aah_correct |> group_by(subject, field, level) |> 
  summarize(rt = median(rt))

rt_descriptive <- rt_subject |>
  group_by(field, level) |>
  summarize(
    median = median(rt),
    mean = mean(rt),
    SE = sd(rt) / sqrt(length((rt)))
  )

g <- ggplot(rt_subject, aes(
  x = level,
  y = rt,
  fill = level,
  color = level
)) +
  geom_quasirandom(alpha = .1, show.legend = F) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = rt_descriptive,
    aes(y = mean),
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(0 , 1500, 100),
                     breaks = seq(0, 1500, 200)) +
  facet_wrap( ~ field) +
  labs(title = "Per-subject medians (RT)", x = "Level", y = "Reaction time (ms)")

g <- g |>  gg_style_means() |> gg_color()
ggsave(fig_path_rt_4, g, "png", height = 4, width = 4)
g_rt_4 <- g
}

#include_graphics(fig_path_rt_4)
```
```{r plot_rt_4a4}
fig_path_rt_4a4 <- here(fig_dir, "rt_combo_4a-4.png")

if (use_cached_rtfigs == FALSE) {
g_rt_4a4 <- g_rt_4a + g_rt_4
ggsave(fig_path_rt_4a4, g_rt_4a4, "png", height = 4, width = 8)
}

include_graphics(fig_path_rt_4a4)
```

```{r plot_rt_2}
fig_path_rt_2 <- here(fig_dir, "rt_2.png")

if (use_cached_rtfigs == FALSE) {
## Make a table showing:
## For each subject and field, the difference in median rt for:
## Global - Local
rt_2 <- rt_subject |> 
  pivot_wider(names_from = c(level),
              values_from = rt) |> 
  mutate(Global_Bias = Local - Global)

rt_descriptive <- rt_2 |>
  group_by(field) |>
  summarize(
    median = median(Global_Bias),
    mean = mean(Global_Bias),
    SE = sd(Global_Bias) / sqrt(length((Global_Bias)))
  )

g <- ggplot(rt_2, aes(x = field,
                      y = Global_Bias, color)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    color = plot_color) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    fill = plot_color,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    show.legend = F
  ) +
  geom_point(
    data = rt_descriptive,
    aes(y = mean),
    fill = plot_color,
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(-500 , 500, 50),
                     breaks = seq(-500, 500, 100)) +
  labs(title = "Global bias (RT)", x = "Level", y = "Local - Global RT (ms)")

g <- g |> gg_style_means()
ggsave(fig_path_rt_2, g, "png", height = 4, width = 4)
g_rt_2 <- g
}

#include_graphics(fig_path_rt_2)
```
```{r plot_rt_1}
fig_path_rt_1 <- here(fig_dir, "rt_1.png")

if (use_cached_rtfigs == FALSE) {
  ## Make a table showing:
  ## For each subject and field, the difference in median rt for:
  ## Global - Local
  rt_1 <- rt_subject |>
    pivot_wider(names_from = c(field, level),
                values_from = rt) |>
    mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
    mutate(all_one_group = "all_one_group")
    
rt_descriptive <- rt_1 |>
  group_by(all_one_group) |> 
  summarize(
    median = median(LVF_Global_Bias),
    mean = mean(LVF_Global_Bias),
    SE = sd(LVF_Global_Bias) / sqrt(length((LVF_Global_Bias)))
  )
rt_descriptive

g <- ggplot(rt_1, aes(
  x = all_one_group,
  y = LVF_Global_Bias,
  fill = plot_colors[[3]],
  color = plot_colors[[3]]
)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    color = plot_color) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    fill = plot_color,
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = rt_descriptive,
    aes(y = mean),
    fill = plot_color,
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(-500 , 500, 50),
                     breaks = seq(-500, 500, 100)) +
  theme(axis.text.x = element_blank()) +
  labs(title = "LVF>RVF Global Bias (RT)", x = "Level", y = "RVF-LVF, Local - Global RT (ms)")

g <- g |> gg_style_means() |> gg_color() +
  theme(axis.text.x = element_blank(), aspect.ratio = 4/1)
ggsave(fig_path_rt_1, g, "png", height = 4, width = 4)
g_rt_1 <- g
}

#include_graphics(fig_path_rt_1)
```
```{r plot_rt_21}
fig_path_rt_21 <- here(fig_dir, "rt_combo_2-1.png")

if (use_cached_rtfigs == FALSE) {
g_rt_1_padded <- g_rt_1 + theme(plot.margin = unit(c(10, 50, 5.5, 40), "pt"))
g_rt_21 <- g_rt_2 + g_rt_1_padded
ggsave(fig_path_rt_21, g_rt_21, "png", height = 4, width = 8)
}

include_graphics(fig_path_rt_21)
```

#### Statistics
Reaction time is modeled as a linear effect of field and level, using data from every trial:
<br>
<br>
`lmer( rt ~ field + level + field:level + (1 | subject) )`
<br>
<br>
*Discussion question*: Should any variables not-of-interest be included as covariates? E.g., sex, target (circle/square), first block (z or slash), overall median rt (ms).
```{r rt_model}
## Make a linear model using data from every trial.
## Fixed effects: field, level (and their interaction)
## Random effects: subject.
## rt ~ field + level + field:level + (1 | subject)
rt_model <- lmer(rt ~ field:level + field + level + (1 | subject), data = aah)

if (use_cached_model_rt == FALSE) {
  ## Create emmeans model object, and manually cache it.
  rt_emm <- emmeans(rt_model, ~ field * level, pbkrtest = 13184)
  
  ## Manually cache model
  saveRDS(rt_emm, here("manual_cache", "rt_emm.rds"))
  
} else if (use_cached_model_rt == TRUE) {
  ## Load cached model
  rt_emm <- readRDS(here("manual_cache", "rt_emm.rds"))
}
```
<!-- Test for field x level interaction, using the anova() function: is the interaction model's fit significantly different from the no-interaction model's fit? -->
<br>
```{r rt_interaction_anova}
## Use anova() on competing models to test 2-way interaction.
interaction_stats <-
  function(model_with_interaction,
           model_with_no_interaction) {
    return(anova(model_with_interaction, model_with_no_interaction))
  }

rt_model_no_interaction <- update(rt_model, . ~ . - field:level)
interaction_anova <- interaction_stats(rt_model, rt_model_no_interaction)
interaction_anova |>
  as_tibble() |>
  rename(p.value = `Pr(>Chisq)`) |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Field by level interaction (RT)", 
             subtitle = "ANOVA: compare models with vs. without interaction term") 
```
<br>
```{r rt_interacion_aov}
## Use aov to test 2-way interaction with a traditional F-test.
rt_aov <- aov(rt ~ field + level + field:level, data = aah)
rt_aov_summary <- summary(rt_aov)
rt_aov_summary |> (\(.) .[[1]])() |> tidy() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (RT)",
             subtitle = "Old-school F-test")
```
<br>
<!-- Test for field x level interaction, using emmeans() - is the model's interaction effect estimate significantly different from zero? -->
```{r rt_interaction_emm}
## Use emmeans() to test 2-way interaction.
rt_interaction_emm <- rt_emm |>
  contrast(interaction = c("consec")) |>
  summary(infer = T)
#rt_interaction_emm

rt_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (RT)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A negative number means global bias is stronger in LVF (as predicted for right handers)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = lower.CL)) |>
  tab_footnote(footnote = "Degrees-of-freedom method: kenward-roger",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_field_bias}
rt_field_bias_emm <- rt_emm |>
  contrast("pairwise") |>
  summary(infer = T, adjust = "none", rows = c(3, 4))
#rt_field_bias_emm

rt_field_bias <- rt_field_bias_emm |>  
  as_tibble() |> 
  filter(contrast %in%
           c("LVF global - LVF local", "RVF global - RVF local"))

rt_field_bias |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Global bias by field (RT)") |>
  tab_footnote(footnote = "A negative number means global bias (faster RT for global)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = lower.CL)) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Degrees-of-freedom method: kenward-roger",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_by_field_level}
rt_modelled <- summary(rt_emm, type = "response")
rt_modelled |>
  as_tibble() |>
  arrange(field) |>
  pretty_table() |>
  tab_header(title = "RT estimates by field and level (from model)") |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = lower.CL)) |>
  tab_footnote(footnote = "Degrees-of-freedom method: kenward-roger",
               locations = cells_column_labels(columns = df))
```
<br>
```{r rt_descriptive}
rt_descriptive <- aah_correct |>
  group_by(field, level) |>
  summarize(
    median = median(rt),
    mean = mean(rt),
    SE = sd(rt) / sqrt(length((rt)))
  )

rt_descriptive |>
  pretty_table() |>
  tab_header(title = "RT estimates by field and level (descriptive)")
```
<br>


### Accuracy
#### Plots
```{r plot_acc_4}
fig_path_acc_4 <- here(fig_dir, "acc_4.png")
fig_path_acc_4_wide <- here(fig_dir, "acc_wide_4.png")

if (use_cached_rtfigs == FALSE) {
acc_subject <- aah |> group_by(subject, field, level) |> 
      summarize(
        total_responses = n(),
        n_present_resp = sum(correct),
        n_absent_resp = total_responses - n_present_resp,
        n_correct = sum(correct),
        acc = 100 * (n_correct / total_responses)
      ) |> 
  select(subject, field, level, acc) |> 
  mutate(level = recode(level, global = "Global", local = "Local"))

acc_descriptive <- acc_subject |>
      group_by(field, level) |> 
      summarize(mean = mean(acc))

g <- ggplot(acc_subject, aes(
  x = level,
  y = acc,
  fill = level,
  color = level
)) +
  geom_quasirandom(alpha = .1, show.legend = F) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = acc_descriptive,
    aes(y = mean),
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(-100, 100, 5),
                     breaks = seq(-100, 100, 10)) +
  facet_wrap( ~ field) +
  labs(title = "Per-subject accuracy", x = "Level", y = "Accuracy (% correct)")

g <- g |> gg_style_means() |> gg_color()
ggsave(fig_path_acc_4, g, "png", height = 4, width = 4)

ggsave(fig_path_acc_4_wide, g, "png", height = 4, width = 8)

g_acc_4 <- g
}

include_graphics(fig_path_acc_4_wide)
```
```{r plot_acc_2}
fig_path_acc_2 <- here(fig_dir, "acc_2.png")

if (use_cached_rtfigs == FALSE) {
## Make a table showing:
## For each subject and field, the difference in median acc for:
## Global - Local
acc_2 <- acc_subject |> 
  pivot_wider(names_from = c(level),
              values_from = acc) |> 
  mutate(Global_Bias = Global - Local)

acc_descriptive <- acc_2 |>
  group_by(field) |>
  summarize(
    median = median(Global_Bias),
    mean = mean(Global_Bias),
    SE = sd(Global_Bias) / sqrt(length((Global_Bias)))
  )

g <- ggplot(acc_2, aes(x = field,
                      y = Global_Bias, color)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    color = plot_color) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    fill = plot_color,
    color = "gray20",
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    show.legend = F
  ) +
  geom_point(
    data = acc_descriptive,
    aes(y = mean),
    fill = plot_color,
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(-100 , 100, 5),
                     breaks = seq(-100, 100, 10)) +
  labs(title = "Global bias (Accuracy)", x = "Level", y = "Local - Global Accuracy (% correct)")

g <- g |> gg_style_means()
ggsave(fig_path_acc_2, g, "png", height = 4, width = 4)
g_acc_2 <- g
}

#include_graphics(fig_path_acc_2)
```
```{r plot_acc_1}
fig_path_ga1 <- here(fig_dir, "acc_1.png")

if (use_cached_accfigs == FALSE) {
  ## Make a table showing:
  ## For each subject and field, the difference in median acc for:
  ## Global - Local
  acc_1 <- acc_subject |>
    pivot_wider(names_from = c(field, level),
                values_from = acc) |>
    mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
    mutate(all_one_group = "all_one_group")
  
acc_descriptive <- acc_1 |>
  group_by(all_one_group) |> 
  summarize(
    median = median(LVF_Global_Bias),
    mean = mean(LVF_Global_Bias),
    SE = sd(LVF_Global_Bias) / sqrt(length((LVF_Global_Bias)))
  )

g <- ggplot(acc_1, aes(
  x = all_one_group,
  y = LVF_Global_Bias
)) +
  geom_quasirandom(
    alpha = .1, show.legend = F,
    color = plot_color) +
  geom_boxplot(
    alpha = 0.5,
    size = 0.3,
    varwidth = F,
    outlier.shape = NA,
    color = "gray20",
    fill = plot_color,
    show.legend = F
  ) +
  stat_summary(
    fun.data = mean_cl_normal,
    fun.args = list(conf.int = 0.95),
    geom = "errorbar",
    position = "dodge",
    linetype = 1,
    color = "gray5",
    width = .2,
    # size = point_size / 5,
    show.legend = F
  ) +
  geom_point(
    data = acc_descriptive,
    aes(y = mean),
    fill = plot_color,
    color = "black",
    shape = 21,
    show.legend = F
  ) +
  scale_y_continuous(minor_breaks = seq(-100 , 100, 5),
                     breaks = seq(-100, 100, 10)) +
  theme(axis.text.x = element_blank()) +
  labs(title = "LVF>RVF Global Bias (Acc.)", x = "Level", y = "LVF-RVF, Global - Local (% correct)")

g <- g |> gg_style_means() |> gg_color() +
  theme(axis.text.x = element_blank(), aspect.ratio = 4/1)
ggsave(fig_path_ga1, g, "png", height = 4, width = 4)
g_acc_1 <- g
}

#include_graphics(fig_path_ga1)
```
```{r plot_acc_21}
fig_path_acc_21 <- here(fig_dir, "acc_combo_21.png")

if (use_cached_rtfigs == FALSE) {
  g_acc_1_padded <- g_acc_1 + theme(plot.margin = 
                              margin(t = 30, r = 50, b = 10, l = 50, unit = "pt"))
  g_acc_21 <- g_acc_2 + g_acc_1_padded
  g_acc_21
  ggsave(fig_path_acc_21, g_acc_21, "png", height = 4, width = 8)
}

include_graphics(fig_path_acc_21)
```

#### Statistics
Accuracy is modeled as a binomial effect of field and level, using data from every trial (correct/incorrect):
<br>
<br>
`glmer( correct ~ field + level + field:level + (1 | subject), family = "binomial" )`
<br>
<br>
```{r acc_model}
## Make a binomial logistic model using data from every trial.
## Fixed effects: field, level (and their interaction)
## Random effects: subject.
## correct ~ field + level + field:level + (1 | subject)
acc_model <- glmer(correct ~ field:level + field + level + (1 | subject),
                   data = aah,
                   family = "binomial")

if (use_cached_model_acc == FALSE) {
  ## Create emmeans model object, and manually cache it.
  acc_emm <- emmeans(acc_model, ~ field * level)
  
  ## Manually cache model
  saveRDS(acc_emm, here("manual_cache", "acc_emm.rds"))
  
} else if (use_cached_model_acc == TRUE) {
  ## Load cached model
  acc_emm <- readRDS(here("manual_cache", "acc_emm.rds"))
}
```
<!-- Test for field x level interaction, using the anova() function: is the interaction model's fit significantly different from the no-interaction model's fit? -->
<br>
```{r acc_interaction_anova}
## Use anova() to test 2-way interaction effect.
interaction_stats <-
  function(model_with_interaction,
           model_with_no_interaction) {
    return(anova(model_with_interaction, model_with_no_interaction))
  }

acc_model_no_interaction <- update(acc_model, . ~ . - field:level)
interaction_anova <- interaction_stats(acc_model, acc_model_no_interaction)
#interaction_anova
interaction_anova |>
  as_tibble() |>
  pretty_table() |> 
  tab_header(title = "Field by level interaction (Accuracy)", 
             subtitle = "ANOVA: compare models with vs. without interaction term") 
```
<br>
<!-- Test for field x level interaction, using emmeans() - is the model's interaction effect estimate significantly different from zero? -->
```{r acc_interaction_emm}
## Is there an interaction of field x level?
## Use an emmeans contrast
acc_interaction_emm <- acc_emm |>
  contrast(interaction = c("consec")) |>
  summary(infer = T, type = "response")
#acc_interaction_emm

acc_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Field by level interaction (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "Backtransformed to odds ratio from log odds ratio; tests are performed on log odds ratio scale.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "I don't understand why df is 'Inf' here, but I think it is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = asymp.LCL)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_field_bias}
acc_field_bias_emm <- acc_emm |>
  contrast("pairwise") |>
  summary(infer = T, adjust = "none", type = "response")
#acc_field_bias_emm

acc_field_bias <- acc_field_bias_emm |>
  as_tibble() |>
  filter(contrast %in%
           c("LVF global / LVF local", "RVF global / RVF local"))
#acc_field_bias

acc_field_bias |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = "Global bias by field (Accuracy)") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio > 1 means global bias (more correct responses for global).",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = asymp.LCL)) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_by_field_level}
acc_modelled <- summary(acc_emm, type = "response")
# acc_modelled
acc_modelled |>
  as_tibble() |> 
  arrange(field) |> 
  pretty_table() |>
  tab_header(title = "Accuracy estimates by field and level (from model)") |>
  tab_footnote(footnote = "Back-transformed to probability (% correct) from logit scale",
               locations = cells_column_labels(columns = prob)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = asymp.LCL))
```
<br>
```{r acc_descriptive}
acc_descriptive <- aah |>
      group_by(level, field, subject) |>
      summarize(
        total_responses = n(),
        n_present_resp = sum(correct),
        n_absent_resp = total_responses - n_present_resp,
        n_correct = sum(correct),
        percent_correct = 100 * (n_correct / total_responses)
      ) |> 
      group_by(field, level) |> 
      summarize(mean_subject_percent_correct = mean(percent_correct))
#acc_descriptive
    
acc_descriptive |>
  pretty_table() |>
  tab_header(title = "Accuracy estimates by field and level (descriptive)")
```
<br>


## Field x Level x Handedness
Once we collect data on lefties, we will test whether LVF-global bias is reduced or reversed with left handedness.
```{r analyze_main_rt}
## Reaction time analyses.
## Linear model using data from every trial.
## (1) Binary handedness. 
## rt ~ target*field*level*handedness

## (2) Continuous handedness

## As a sanity check, do parallel analyses with summary rt data instead of trial-level data.
```

```{r analyse_main_acc}
```

<!-- ## Visualize individual results -->
```{r visualize_individual_rt}
## Visualize per-trial RT data (make absent one color, present another)

```

<!-- ## Visualize group results -->
```{r}
## ## Visualize RT data by condition
```

```{r visualize_group_acc}
## Visualize accuracy data by condition
```

